\documentclass{ctexart}
\usepackage[a4paper,left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry}
\usepackage{amssymb,amsfonts,amsmath,amsthm}
\usepackage{anyfontsize}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{bm}
\usepackage{bbm}
\usepackage{mathrsfs}
\usepackage[colorlinks = true,      % 启用彩色链接而非带框链接
            linkcolor = blue,       % 内部链接（如目录、交叉引用）颜色
            urlcolor = blue,        % 外部链接颜色
            citecolor = blue]{hyperref} % 参考文献链接颜色

\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{setting}{Setting}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{reason}{Reason}[section]
\newtheorem{example}{Example}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{exercise}{Exercise}[section]

\renewcommand{\proofname}{\textit{Proof}}
\renewcommand{\contentsname}{Contents}
\renewcommand{\refname}{References}
\renewcommand{\hom}{\operatorname{Hom}}

\newcommand{\leftquotes}{``}
\newcommand{\rightquotes}{''}

\newcommand{\mapsfrom}{\mathrel{\reflectbox{\ensuremath{\mapsto}}}}
\newcommand{\longmapsfrom}{\mathrel{\reflectbox{\ensuremath{\longmapsto}}}}

\newcommand{\rank}{\operatorname{rank}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\identity}{\operatorname{id}}
\newcommand{\trdeg}{\operatorname{trdeg}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\depth}{\operatorname{depth}}
\newcommand{\height}{\operatorname{height}}
\newcommand{\projdim}{\dim_{\operatorname{proj}}}
\newcommand{\characteristic}{\operatorname{Char}}

\newcommand{\derivation}{\operatorname{Der}}
\newcommand{\ext}{\operatorname{Ext}}
\newcommand{\mor}{\operatorname{Mor}}
\newcommand{\aut}{\operatorname{Aut}}
\newcommand{\homend}{\operatorname{End}}

\newcommand{\sheafhom}{\mathcal{H}\kern -.5pt om}
\newcommand{\sheaftor}{\mathcal{T}\kern -.5pt or}
\newcommand{\sheafext}{\mathcal{E}\kern -.5pt xt}
\newcommand{\sheafend}{\mathcal{E}\kern -.5pt nd}

\newcommand{\coker}{\operatorname{coker}}
\newcommand{\coim}{\operatorname{coim}}
\newcommand{\cone}{\operatorname{cone}}
\newcommand{\exceptionallocus}{\operatorname{Ex}}
\newcommand{\totalcomplex}{\operatorname{Tot}}

\newcommand{\spec}{\operatorname{Spec}}
\newcommand{\proj}{\operatorname{Proj}}
\newcommand{\spf}{\operatorname{Spf}}
\newcommand{\fraction}{\operatorname{Frac}}
\newcommand{\singular}{\operatorname{Sing}}
\newcommand{\support}{\operatorname{Supp}}
\newcommand{\framebundle}{\operatorname{Fr}}

\newcommand{\reduction}{\operatorname{red}}
\newcommand{\normalization}{\operatorname{nor}}
\newcommand{\regular}{\operatorname{reg}}
\newcommand{\smooth}{\operatorname{sm}}
\newcommand{\analytification}{\operatorname{an}}

\newcommand{\inverselimit}{\underset{\longleftarrow}{\lim}} 
\newcommand{\colimit}{\underset{\longrightarrow}{\lim}}
\newcommand{\derivedotimes}{\overset{\llcorner}{\otimes}}

\newcommand{\grassmannianscheme}[2]{\operatorname{Gr}(#1, #2)}
\newcommand{\grassmanmianfunctor}[2]{\mathcal{G}\kern -.5pt r(#1, #2)}
\newcommand{\hilbertscheme}{\operatorname{Hilb}}
\newcommand{\hilbertfunctor}{\mathcal{H}\kern -.5pt ilb}
\newcommand{\picardscheme}{\operatorname{Pic}}
\newcommand{\picardfunctor}{\mathcal{P}\kern -.5pt ic}
\newcommand{\isomorphismscheme}{\operatorname{Isom}}
\newcommand{\isomorphismfunctor}{\mathcal{I}\kern -.5pt som}

\newcommand{\abeliangroups}{\mathbf{Ab}}
\newcommand{\rings}{\mathbf{Ring}}
\newcommand{\commutativerings}{\mathbf{CRing}}
\newcommand{\sets}{\mathbf{Set}}

\newcommand{\module}{\mathbf{Mod}}
\newcommand{\vectorspace}{\mathbf{Vect}}
\newcommand{\algebra}{\mathbf{Alg}}
\newcommand{\scheme}{\mathbf{Sch}}
\newcommand{\vectorbundle}{\underline{\mathbf{Vect}}}
\newcommand{\coherent}{\mathbf{Coh}}
\newcommand{\quasicoherent}{\mathbf{Qcoh}}

\newcommand{\matrices}[2]{\operatorname{Mat}_{#1}(#2)}
\newcommand{\generallineargroup}[2]{\operatorname{GL}_{#1}(#2)}
\newcommand{\speciallineargroup}[2]{\operatorname{SL}_{#1}(#2)}
\newcommand{\projectivespeciallineargroup}[2]{\operatorname{PSL}_{#1}(#2)}

\newcommand{\order}{\operatorname{ord}}
\newcommand{\divisor}{\operatorname{div}}
\newcommand{\annihilator}{\operatorname{ann}}

\title{Vector Bundles on Curves}
\author{Taught by Jiabin Du}
\date{}

\begin{document}
\maketitle
\newpage

\tableofcontents
\newpage

\section*{Introduction}
\label{section:Introduction}

The course aims at introducing vector bundles on curve and Koszul cohomology.
You may benefit from the following references
\begin{itemize}
    \item \emph{Koszul Cohomology and Algebraic Geometry}, Aprodu-Nagel
    \item \emph{Lectures on Vector Bundles}, J.Le Potier
    \item \emph{The Geometry of Moduli Space of Sheaves}, Huybrechts-Lehn.
\end{itemize}

\section{Vector Bundles}
\label{section:Vector_Bundles}

\subsection{Sheaf theory}
\label{subsection:Vector_Bundles_Sheaf_theory}

Recall the definition of sheaves.
\begin{definition}
    Let $X$ be a topological space and $\mathcal{C}$ be a category.
    Assume $op(X)$ is the category of open subsets of X with morphisms are inclusions.
    A presheaf on $X$ valued on $\mathcal{C}$ (or say of $\mathcal{C}$) is a contravariant functor $\mathcal{F}: op(X) \longrightarrow \mathcal{C}$.
\end{definition}
\begin{remark}
    Though we can consider this general definition of presheaf, we would only consider presheaves at least valued on $Ab$,
    where $Ab$ is the category of abelian groups.
    In addition, we need these presheaves map $\varnothing$ to $\{0\}$.
\end{remark}
\begin{definition}
    Let $X$ be a topological space, $\mathcal{F}$ presheaf of abelian groups on $X$.
    For $V \subseteq V$, we call the correspondence homomorphism $\mathcal{F}(U) \longrightarrow \mathcal{F}(V)$ a restriction map, denoted by $\cdot \rho_{UV}$.
    Elements in $\mathcal{F}(U)$ is called a section of $\mathcal{F}$ on $U$.
    In particular, if $U = X$, we call elements of $\mathcal{F}(X)$ global sections, otherwise local sections.
\end{definition}
\begin{remark}
    For convenience, for $s\in \mathcal{F}(U)$, we would write $s\big{|}_V$ to denote image of $s$ instead of $\rho_{UV}(s)$.
    Also, sometimes $\mathcal{F}(U)$ can be rewritten as $\Gamma(U, \mathcal{F})$.
\end{remark}
\begin{definition}
    Let $X$ be a topological space, $\mathcal{F}$ presheaf of abelian groups on $X$.
    $\mathcal{F}$ is a sheaf on $X$ if it satisfies that \\
    (1)For each open subset $U$ with open covering $\{U_{i}\}_{i\in I}$ and $s\in \mathcal{F}(U)$, 
    if $s\big{|}_{U_{i}} = 0$ for all $i$, then $s = 0$. \\
    (2)For each open subset $U$ with open covering $\{U_{i}\}_{i\in I}$,
    if there exists $s_{i}\in \mathcal{F}(U_{i})$ for all $i$, satisfying $s_{i}\big{|}_{U_{i} \cap U_{j}} = s_{j}\big{|}_{U_{i} \cap U_{j}}$ for all $i,j$,
    then there exists $s\in \mathcal{F}(U)$ such that $s\big{|}_{U_{i}} = s_{i}$ for all $i$.
\end{definition}
\begin{remark}
    The two conditions in fact give a exact sequence for each open subset $U$ with open covering $\{U_{i}\}_{i\in I}$.
    \begin{equation}
        0 \longrightarrow \mathcal{F}(U) \longrightarrow \prod_{i\in I} \mathcal{F}(U_{i}) \longrightarrow \prod_{i,j\in I} \mathcal{F}(U_{i} \cap U_{j})
    \end{equation}
\end{remark}
\begin{example}
    (1)Let $X$ be a topological space.
    Then $U \longmapsto \{\text{continuous functions $U \longrightarrow \mathbb{R}$}\}$ give a sheaf on $X$. \\
    (2)Let $X = \mathbb{R}^{n}$.
    Then $U \longmapsto \{\text{$C^{\infty}$-functions $U \longrightarrow \mathbb{R}$}\}$ gives a sheaf on $X$. \\
    (3)Let $X$ be a topological space and $A$ be an abelian group.
    View $A$ as a topological space with discrete topology.
    Then $U \longmapsto \{\text{locally constant functions $U \longrightarrow A$}\}$ gives a sheaf on $X$, which is called the constant sheaf of $A$ on $X$.
\end{example}
\begin{definition}
    Let $X$ be a topological space, $\mathcal{F}$ (pre)sheaf of abelian groups on $X$.
    For $x\in X$, define the stalk of $\mathcal{F}$ at $x$ to be $\mathcal{F}_{x} = \underset{\underset{U\ni x}{\longrightarrow}}{\lim} \mathcal{F}(U)$.
    More concretely, an element of $\mathcal{F}_{x}$ is represented by a pair $(U, s) = s_{x}$ where $U$ is an open neighbourhood of x and $s\in \mathcal{F}(U)$, called a germ.
    Two germs $(U, s)$ and $(V, t)$ represent the same element if there exists open neighbourhood $W$ of $x$ such that $W \subseteq U \cap V$ and $s\big{|}_{W} = t\big{|}_{W}$.
\end{definition}
\begin{proposition}
    Let $X$ be a topological space, $\mathcal{F}$ sheaf of abelian groups on $X$.
    Suppose $U$ is an open subset of $X$ and $s,t\in \mathcal{F}(U)$.
    Then $s = t$ if and only if $s_{x} = t_{x}$ for all $x\in U$.
    \label{Proposition 1.1}
\end{proposition}
\begin{proof}
    $\leftquotes \Rightarrow \rightquotes$: Obviously.
    \par
    $\leftquotes \Leftarrow \rightquotes$: Since for all $x\in U$, we have $s_{x} = t_{x}$,
    there exists open neighbourhood $W_{x}$ of $x$ such that $W_{x} \subseteq U$ and $s\big{|}_{W_{x}} = t\big{|}_{W_{x}}$.
    Note that $\{W_{x}\}_{x\in U}$ form an open covering of $U$.
    By property of sheaf, we get $s = t$.
\end{proof}
\begin{definition}
    Let $X$ be a topological space, $\mathcal{F}, \mathcal{G}$ (pre)sheaves of abelian groups on $X$.
    A morphism $\varphi$ from $\mathcal{F}$ to $\mathcal{G}$ is a family of group homomorphisms $\varphi(U): \mathcal{F}(U) \longrightarrow \mathcal{G}(U)$ such that for $V \subseteq U$,
    there is a commutative diagram
    \begin{equation}
        \begin{tikzcd}
            \mathcal{F}(U) \arrow[r, "\varphi(U)"] \arrow[d, "\rho_{UV}"] &
            \mathcal{G}(U) \arrow[d, "\rho_{UV}"] \\
            \mathcal{F}(V) \arrow[r, "\varphi(V)"] &
            \mathcal{G}(V)
        \end{tikzcd}
    \end{equation}
\end{definition}
\begin{remark}
    By property of direct limit, morphism $\varphi$ gives homomorphism $\varphi_{x}: \mathcal{F}_{x} \longrightarrow \mathcal{G}_{x}$ for all $x\in X$.
\end{remark}
\begin{definition}
    Let $X$ be a topological space, $\varphi: \mathcal{F} \longrightarrow \mathcal{G}$ morphism of (pre)sheaves of abelian groups on $X$.
    We say $\varphi$ is isomorphic if there exists morphism $\psi: \mathcal{G} \longrightarrow \mathcal{F}$ such that for each open subsets $U$, 
    $\psi(U)\varphi(U) = \identity_{\mathcal{F}(U)}$ and $\varphi(U)\psi(U) = \identity_{\mathcal{G}(U)}$.
\end{definition}
\begin{proposition}
    Let $X$ be a topological space, $\varphi: \mathcal{F} \longrightarrow \mathcal{G}$ morphism of sheaves of abelian groups on $X$.
    Then $\varphi$ is isomorphic if and only if $\varphi_{x}$ is isomorphic for all $x\in X$.
    \label{Proposition 1.2}
\end{proposition}
\begin{proof}
    "$\Rightarrow$": For all $(U, t)\in \mathcal{F}_{x}$, since $\varphi(V)$ is isomorphic,
    there exists $s\in \mathcal{F}(U)$ such that $\varphi(V)(s) = t$.
    Thus $\varphi_{x}((U, s)) = (U, t)$, get $\varphi_{x}$ is surjective.
    For all $(U, s)\in \ker(\varphi_{x})$, $(U, \varphi(U)(s)) = 0$ in $\mathcal{G}_{x}$.
    Then there exists open neighbourhood $V$ of $x$ such that $V \subseteq U$ and $\varphi(U)(s)\big{|}_{V} = 0$.
    By commutative diagram, $\varphi(U)(s)\big{|}_{V} = \varphi(V)(s\big{|}_{V})$.
    Since $\varphi(V)$ is isomorphic, get $s\big{|}_{V} = 0$ and so $(U, s) = 0$ in $\mathcal{F}_{x}$.
    Get $\varphi_{x}$ is isomorphic.
    \par
    "$\Leftarrow$": For each open subset $U$, want to show that $\varphi(U)$ is isomorphic.
    For $s\in \ker{\varphi(U)}$, $\varphi(U)(s) = 0$.
    Then for all $x\in U$, $(U, \varphi(U)(s)) = 0$ in $\mathcal{G}_{x}$.
    As $(U, \varphi(U)(s)) = \varphi_{x}((U, s))$ and $\varphi_{x}$ is isomorphic, get $(U, s) = 0$ in $\mathcal{F}_{x}$.
    Thus there exists open neighbourhood $W_{x}$ of $x$ such that $W_{x} \subseteq U$ and $s\big{|}_{W_{x}} = 0$.
    By property of sheaf, get $s = 0$ and so $\varphi(U)$ is injective.
    \par
    For all $t\in \mathcal{G}(U)$, $(U, t)$ is an element of $\mathcal{G}_{x}$ for all $x\in U$.
    Then there exists $(V_{x}, s(x))\in \mathcal{F}_{x}$ such that $\varphi_{x}((V_{x}, s(x))) = (U, t)$ and $\varphi(V_{x})(s(x)) = t\big{|}_{V_{x}}$.
    Note that $\varphi(V_{x} \cap V_{y})(s(x)\big{|}_{V_{x} \cap V_{y}}) = (t\big{|}_{V_{x}})\big{|}_{V_{x} \cap V_{y}} = (t\big{|}_{V_{y}})\big{|}_{V_{x} \cap V_{y}} = \varphi(V_{x} \cap V_{y})(s(y)\big{|}_{V_{x} \cap V_{y}})$.
    Since $\varphi(V_{x} \cap V_{y})$ is injective, get $s(x)\big{|}_{V_{x} \cap V_{y}} = s(y)\big{|}_{V_{x} \cap V_{y}}$.
    By property of sheaf, there exists $s\in \mathcal{F}(U)$ such that $s\big{|}_{V_{x}} = s(x)$.
    So $\varphi(U)(s)\big{|}_{V_{x}} = \varphi(V_{x})(s(x)) = t\big{|}_{V_{x}}$.
    By property of sheaf, get $\varphi(U)(s) = t$ and so $\varphi(U)$ is isomorphic.
\end{proof}
\begin{definition}
    Let $X$ be a topological space, $\varphi: \mathcal{F} \longrightarrow \mathcal{G}$ morphism of presheaves of abelian groups on $X$.
    We have several notions
    \begin{itemize}
        \item Define the kernel of $\varphi$ to be $\ker(\varphi): op(X) \longrightarrow Ab\quad U \longmapsto \ker(\varphi(U))$.
        \item Define the image of $\varphi$ to be $im(\varphi): op(X) \longrightarrow Ab\quad U \longmapsto im(\varphi(U))$.
        \item Define the cokernel of $\varphi$ to be $coker(\varphi): op(X) \longrightarrow Ab\quad U \longmapsto coker(\varphi(U))$.
    \end{itemize}
\end{definition}
\begin{remark}
    The definition of cokernel in fact induce the definition of quotient presheaf.
\end{remark}
\begin{definition}[\textbf{\emph{Sheafification}}]
    Let $X$ be a topological space, $\mathcal{F}$ presheaf of abelian groups on $X$.
    Define a sheaf $\mathcal{F}^{+}$ of abelian groups on $X$ by $U \longmapsto \mathcal{F}^{+}(U)$, 
    where $\mathcal{F}^{+}(U) = \{(s_{x})_{x\in U} \big{|} \text{ for all $x\in U$, $\exists$ \text{open} $V_{x}\ni x$ and $t(x)\in \mathcal{F}(V_{x})$ such that $t(x)_{y} = s_{y}$, $\forall y\in V_{x}$}\}$ is a subset of $\prod_{x\in U} \mathcal{F}_{x}$.
\end{definition}
\begin{proposition}
    Let $X$ be a topological space, $\mathcal{F}$ presheaf of abelian groups on X.
    Show that there is a natural morphism of presheaves $\varphi: \mathcal{F} \longrightarrow \mathcal{F}^{+}$ satisfies that
    \begin{itemize}
        \item $\varphi_{x}$ is identity homomorphism.
        \item If $\mathcal{F}$ is sheaf, then $\varphi$ is isomorphism.
        \item For any morphism of presheaves $\psi: \mathcal{F} \longrightarrow \mathcal{G}$ where $\mathcal{G}$ is a sheaf,
        there exists unique morphism $\phi: \mathcal{F}^{+} \longrightarrow \mathcal{G}$ such that the following diagram commutes.
        \begin{equation}
            \begin{tikzcd}
                \mathcal{F} \arrow[rr, "\psi"] \arrow[dr, "\varphi"] &&
                \mathcal{G} \\
                & \mathcal{F}^{+} \arrow[ur, "\phi"] &
            \end{tikzcd}
        \end{equation}
    \end{itemize}
    \label{Proposition 1.3}
\end{proposition}
\begin{reason}
    The construction of $\varphi$ is just $\varphi(U): s \longmapsto (s_{x})_{x\in U}$.
\end{reason}
\begin{definition}
    Let $X$ be a topological space, $\varphi: \mathcal{F} \longrightarrow \mathcal{G}$ morphism of sheaves of abelian groups on X. \\
    (1)Define the kernel of $\varphi$ to be $\ker(\varphi): op(X) \longrightarrow Ab\quad U \longmapsto \ker(\varphi(U))$. \\
    (2)Define the image of $\varphi$ to be sheafification of $op(X) \longrightarrow Ab\quad U \longmapsto im(\varphi(U))$, denoted by $im(\varphi)$. \\
    (3)Define the cokernel of $\varphi$ to be sheafification of $op(X) \longrightarrow Ab\quad U \longmapsto coker(\varphi(U))$, denoted by $coker(\varphi)$.
\end{definition}
\begin{remark}
    The definition of cokernel in fact induce the definition of quotient sheaf.
\end{remark}
\begin{definition}
    Let $X$ be a topological space, $\varphi: \mathcal{F} \longrightarrow \mathcal{G}$ morphism of sheaves of abelian groups on X. \\
    (1)We say that $\varphi$ is injective if $\ker(\varphi) = 0$. \\
    (2)We say that $\varphi$ is surjective if $im(\varphi) = \mathcal{G}$
\end{definition}
\begin{proposition}
    Let $X$ be a topological space, $\varphi: \mathcal{F} \longrightarrow \mathcal{G}$ morphism of sheaves of abelian groups on X.
    Then \\
    (1)$\varphi$ is injective if and only if $\varphi(U)$ is injective for all open subset U. \\
    (2)$\varphi$ is injective if and only if $\varphi_{x}$ is injective for all $x\in X$. \\
    (3)$\varphi$ is surjective if and only if $\varphi_{x}$ is surjective for all $x\in X$. \\
    (4)$\varphi$ is isomorphic if and only if $\varphi$ is injective and surjective.
    \label{Proposition 1.4}
\end{proposition}
\begin{remark}
    The proof is similar to proof of Proposition \ref{Proposition 1.2}.
    In addition, Hartshorne exercise II 1.2 gives a more explicit sketch.
\end{remark}
\begin{definition}[\textbf{\emph{Direct Image and Inverse Image}}]
    Let $f:X \longrightarrow Y$ be continuous map of topological spaces, $\mathcal{F}$ sheaf of abelian groups on X, $\mathcal{G}$ sheaf of abelian groups on Y. \\
    (1)Define dierct image to be the sheaf $f_{\ast}\mathcal{F}: V \longmapsto f_{\ast}\mathcal{F}(V) = \mathcal{F}(f^{-1}(V))$. \\
    (2)Define inverse image to be the sheafification of $U \longmapsto \underset{\underset{V \supseteq f(U)}{\longrightarrow}}{\lim} \mathcal{G}(V)$, denoted by $f^{-1}\mathcal{G}$.
\end{definition}
\begin{remark}
    In general, we don't have $(f_{\ast}\mathcal{F})_{f(x)} \neq \mathcal{F}_{x}$,
    while there is a canonical homomorphism $(f_{\ast}\mathcal{F})_{f(x)} \longrightarrow \mathcal{F}_{x}$.
    On the other hand, we always have $(f^{-1}\mathcal{G})_{x} = \mathcal{G}_{f(X)}$.
\end{remark}
\begin{example}
    Let $i: Z \hookrightarrow X$ be an inclusion of topological spaces, $\mathcal{F}$ sheaf of abelian groups on X.
    We often write $i^{-1}\mathcal{F}$ as $\mathcal{F}\big{|}_{Z}$.
\end{example}

\subsection{Sheaf modules}
\label{subsection:Vector_Bundles_Sheaf_modules}

\begin{definition}
    Let $X$ be a scheme or $(X, \mathcal{O}_{X})$ be a ringed space.
    A sheaf of $\mathcal{O}_{X}$-modules is a sheaf of abelian groups $\mathcal{F}$ on X such that for all $U \subseteq X$ open, 
    $\mathcal{F}(U)$ is a module over $\mathcal{O}_{X}(U)$ which is compatible with restriction maps.
\end{definition}
\begin{definition}
    Let $X$ be a scheme or $(X, \mathcal{O}_{X})$ be a ringed space, $\mathcal{F},\mathcal{G}$ two $\mathcal{O}_{X}$-modules.
    A morphism $\varphi$ from $\mathcal{F}$ to $\mathcal{G}$ is a morphism of sheaves compatible with the module structure i.e. for all $U \subseteq X$ open, 
    $\varphi(U): \mathcal{F}(U) \longrightarrow \mathcal{G}(U)$ is a homomorphism of $\mathcal{O}_{X}(U)$-modules.
\end{definition}
\begin{remark}
    Kernel, image and cokernel of a morphism of $\mathcal{O}_{X}$-modules are still $\mathcal{O}_{X}$-modules.
    Can also define submodule, quotient module and direct sum.
\end{remark}
\begin{definition}
    Let $X$ be a scheme or $(X, \mathcal{O}_{X})$ be a ringed space.
    An sheaf ideal on X is an $\mathcal{O}_{X}$-submodule of $\mathcal{O}_{X}$.
\end{definition}
\begin{definition}[\textbf{\emph{Tensor Products}}]
    Let $X$ be a scheme or $(X, \mathcal{O}_{X})$ be a ringed space, $\mathcal{F},\mathcal{G}$ two $\mathcal{O}_{X}$-modules.
    Define tensor product $\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{G}$ to be the sheafification of $U \longmapsto \mathcal{F}(U) \otimes_{\mathcal{O}_{X}(U)} \mathcal{G}(U)$.
\end{definition}
\begin{remark}
    The stalk of $\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{G}$ at $x\in X$ is just $\mathcal{F}_{x} \otimes_{\mathcal{O}_{X, x}} \mathcal{G}_{x}$.
\end{remark}
\begin{definition}[\textbf{\emph{Free $\mathcal{O}_{X}$-modules}}]
    Let $X$ be a scheme or $(X, \mathcal{O}_{X})$ be a ringed space, $\mathcal{F}$ an $\mathcal{O}_{X}$-module.
    We say that $\mathcal{F}$ is free if $\mathcal{F}$ is isomorphic to a direct sum of $\mathcal{O}_{X}$.
    In addition, we say that $\mathcal{F}$ is free of rank r if $\mathcal{F} \cong \mathcal{O}_{X}^{r}$.
\end{definition}
\begin{definition}[\textbf{\emph{Locally Free $\mathcal{O}_{X}$-modules}}]
    Let $X$ be a scheme or $(X, \mathcal{O}_{X})$ be a ringed space, $\mathcal{F}$ an $\mathcal{O}_{X}$-module.
    We say that $\mathcal{F}$ is locally free if X can be covered by open subsets $\{U_{i}\}_{i\in I}$ such that $\mathcal{F}\big{|}_{U_{i}}$ is free as $\mathcal{O}_{U_{i}}$-module.
    In addition, we say that $\mathcal{F}$ is locally free of rank r if X can be covered by open subsets $\{U_{i}\}_{i\in I}$ such that $\mathcal{F}\big{|}_{U_{i}} \cong \mathcal{O}_{U_{i}}^{r}$ as $\mathcal{O}_{U_{i}}$-module.
\end{definition}
\begin{definition}[\textbf{\emph{Invertible $\mathcal{O}_{X}$-modules}}]
    Let $X$ be a scheme or $(X, \mathcal{O}_{X})$ be a ringed space, $\mathcal{F}$ an $\mathcal{O}_{X}$-module.
    We say that $\mathcal{F}$ is invertible if it is locally free of rank 1.
\end{definition}
\begin{remark}
    If take $\mathcal{G} = \sheafhom_{\mathcal{O}_{X}}(\mathcal{F}, \mathcal{O}_{X})$, then $\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{G} \cong \mathcal{O}_{X}$.
\end{remark}
\begin{lemma}
    Let $f: X \longrightarrow Y$ be a morphism of schemes or ringed spaces, $\mathcal{F}$ an $\mathcal{O}_{X}$-module, $\mathcal{G}$ an $\mathcal{O}_{Y}$-module.
    Then the direct image $f_{\ast}\mathcal{F}$ of $\mathcal{F}$ is an $\mathcal{O}_{Y}$-module induced by $f^{\sharp}$.
    On the other hand, the inverse image $f^{\ast}\mathcal{G} = f^{-1}\mathcal{G} \otimes_{f^{-1}\mathcal{O}_{Y}} \mathcal{O}_{X}$ of $\mathcal{G}$ is an $\mathcal{O}_{X}$-module where $f^{-1}\mathcal{O}_{Y} \longrightarrow \mathcal{O}_{X}$ is induced by $f^{\sharp}$.
    \label{Lemma 1.1}
\end{lemma}

\subsection{Quasi-coherent and coherent sheaves}
\label{subsection:Vector_Bundles_Quasi-coherent_and_coherent_sheaves}

\begin{definition}
    Let $A$ be a ring, $X = \spec A$, $M\in \module_{A}$.
    Define an $\mathcal{O}_{X}$-module $\widetilde{M}$ on $X$ by the same process as $\mathcal{O}_{X}$ replacing $A$ by $M$.
\end{definition}
\begin{remark}
    The definition gives a fully faithful functor from $\module_{A}$ to category of $\mathcal{O}_{Spec(A)}$-modules $M \longmapsto \widetilde{M}$.
\end{remark}
\begin{proposition}
    Let $A$ be a ring, $X = \spec A$, $M\in \module_{A}$.
    Then \\
    (1)$\widetilde{M}(X) = M$, \\
    (2)$\widetilde{M}(D(f)) = M_{f} = M \otimes_{A} A_{f}$ \\
    (3)$\widetilde{M}_{\mathfrak{p}} = M_{\mathfrak{p}} = M \otimes_{A} A_{\mathfrak{p}}$.
    \label{Proposition 1.5}
\end{proposition}
\begin{proposition}
    Let $A$ be a ring, $X = \spec A$.
    Then \\
    (1)Let $M_{i}$ be $A$-modules. 
    Then $\widetilde{\oplus_{i} M_{i}} \cong \oplus_{i} \widetilde{M_{i}}$. \\
    (2)Let M,N be $A$-modules.
    Then $\widetilde{M \otimes_{A} N} \cong \widetilde{M} \otimes_{\mathcal{O}_{X}} \widetilde{N}$. \\
    (3)Let $L,M,N$ be $A$-modules.
    Then $L \longrightarrow M \longrightarrow N$ is exact if and only if $\widetilde{L} \longrightarrow \widetilde{M} \longrightarrow \widetilde{N}$ is exact. \\
    (4)Let $f: \spec(B) \longrightarrow \spec A$ be a morphism of affine schemes corresponding to ring homomorphism $\varphi: A \longrightarrow B$, $M\in Mod_{A}$, $N\in Mod_{B}$.
    Then $f_{\ast}\widetilde{N} \cong \widetilde{N}$, where $N$ is viewed as $A$-module, and $f^{\ast}\widetilde{M} \cong \widetilde{M \otimes_{A} B}$.
    \label{Proposition 1.6}
\end{proposition}
\begin{definition}[\textbf{\emph{Quasi-coherent Sheaves}}]
    Let $X$ be a scheme, $\mathcal{F}$ a sheaf of abelian groups on $X$.
    We say that $\mathcal{F}$ is quasi-coherent if for all affine open subset $U = \spec A \subseteq X$,
    $\mathcal{F}\big{|}_{U} \cong \widetilde{M}$ for some $A$-module $M$.
\end{definition}
\begin{definition}[\textbf{\emph{Coherent Sheaves}}]
    Let $X$ be a noetherian scheme, $\mathcal{F}$ a sheaf of abelian groups on $X$.
    We say that $\mathcal{F}$ is coherent if for all affine open subset $U = \spec A \subseteq X$,
    $\mathcal{F}\big{|}_{U} \cong \widetilde{M}$ for some finite $A$-module $M$.
\end{definition}
\begin{theorem}
    Let $X$ be a scheme, $\mathcal{F}$ an $\mathcal{O}_{X}$-module.
    Suppose $X$ admits an affine open subset covering $\{U_{i} = \spec(A_{i})\}_{i}$ such that for all $i$, $\mathcal{F}\big{|}_{U_{i}} \cong \widetilde{M_{i}}$ for some $A_{i}$-module $M_{i}$.
    Then $\mathcal{F}$ is quasi-coherent.
    If moreover $X$ is noetherian and $M_{i}$ are finite over $A_{i}$, then $\mathcal{F}$ is coherent.
    \label{Theorem 1.1} 
\end{theorem}
\begin{proof}
    Let $U = \spec A \subseteq X$ be an affine open subset.
    Cover each $U \cap U_{i}$ with $\{U_{ik}\}$ such that $U_{ik} \subseteq U_{i}$ of the form $D(g_{ik})$.
    Then $\mathcal{F}\big{|}_{U_{ik}} \cong \widetilde{{M_{i}}_{g_{ik}}}$.
    Can assume $X = U = \spec A$ and finitely many affine open subset $U_{i}$ such that $\mathcal{F}\big{|}_{U_{i}} \cong \widetilde{M_{i}} = \widetilde{\mathcal{F}(U_{i})}$.
    \par
    To prove $\mathcal{F} \cong \widetilde{\mathcal{F}(X)}$, it suffices to show that for all $f\in A$, $\mathcal{F}(X)_{f} = \mathcal{F}(X) \otimes_{A} A_{f} \longrightarrow \mathcal{F}(D(f))$ is isomorphic.
    Set $V_{i} = U_{i} \cap D(f) = D(f\big{|}_{U_{i}})$.
    As tensor product commutes with finite direct sum, there is commutative diagram with exact rows,
    \begin{equation}
        \begin{tikzcd}
            0 \arrow[r] &
            \mathcal{F}(X)_{f} \arrow[r] \arrow[d] &
            \prod_{i} \mathcal{F}(U_{i})_{f} \arrow[r] \arrow[d] &
            \prod_{i,j} \mathcal{F}(U_{i} \cap U_{j})_{f} \arrow[d] \\
            0 \arrow[r] &
            \mathcal{F}(D(f)) \arrow[r] &
            \prod_{i} \mathcal{F}(V_{i}) \arrow[r] &
            \prod_{i,j} \mathcal{F}(V_{i} \cap V_{j})
        \end{tikzcd}
    \end{equation}
    Similar to proof of Lemma \ref{Lemma 2.6}, get $\mathcal{F}$ is quasi-coherent.
    \par
    Further if $A$ is noetherian, $\mathcal{F} = \widetilde{M}$.
    Can cover $X$ by finitely many $\{D(f_{i})\}$ such that $\mathcal{F}(D(f_{i})) = M_{f_{i}}$ is finite over $A_{f_{i}}$
    Assume $M_{f_{i}} = \sum_{j} \frac{m_{ij}}{1}A_{f_{i}}$.
    Take $N = \sum_{i,j} m_{i,j}A$.
    Then $N$ is a finitely generated A-submodule of $M$ and for all $i$, $N_{f_{i}} = M_{f_{i}}$.
    Thus there is a natural morphism $\widetilde{N} \longrightarrow \widetilde{M}$ and $\widetilde{N}\big{|}_{D(f_{i})} \overset{\sim}{\longrightarrow} \widetilde{M}\big{|}_{D(f_{i})}$ is isomorphic for all $i$.
    As $d(f)_{i}$ cover $X$, get $\widetilde{N} \longrightarrow \widetilde{M}$ is isomorphic so that $N = M$ and M is finitely generated.
    Thus $\mathcal{F}$ is coherent.
\end{proof}
\begin{proposition}
    Let $X$ be a scheme.
    Then \\
    (1)Kernel, image and cokernel of morphism of quasi-coherent sheaves are still quasi-coherent. \\
    (2)Direct sum of quasi-coherent sheaves is quasi-coherent. \\
    (3)Tensor product of two quasi-coherent sheaves is quasi-coherent.
    \label{Proposition 1.7}
\end{proposition}
\begin{remark}
    If $X$ is moreover noetherian, then (1) and (3) still hold for coherent and (2) is also ok if the direct sum is finite.
\end{remark}
\begin{proposition}
    Let $X$ be an affine scheme.
    Then for all exact sequence of quasi-coherent sheaves 
    \begin{equation}
        0 \longrightarrow \mathcal{F} \longrightarrow \mathcal{G} \longrightarrow \mathcal{H} \longrightarrow 0
    \end{equation}
    the sequence of global sections 
    \begin{equation}
        0 \longrightarrow \mathcal{F}(X) \longrightarrow \mathcal{G}(X) \longrightarrow \mathcal{H}(X) \longrightarrow 0
    \end{equation}
    is exact.
    \label{Proposition 1.8}
\end{proposition}
\begin{proposition}
    Let $X$ be a scheme, $\mathcal{F}$ an $\mathcal{O}_{X}$-module.
    Then $\mathcal{F}$ is quasi-coherent if and only if for all $x\in X$, 
    there exists open neighbourhood $U\ni x$ such that there is an exact sequence
    \begin{equation}
        \mathcal{O}_{U}^{\oplus J} \longrightarrow \mathcal{O}_{U}^{\oplus I} \longrightarrow \mathcal{F}\big{|}_{U} \longrightarrow 0
    \end{equation}
    If moreover $X$ is noetherian,
    then $\mathcal{F}$ is coherent if and only if for all $x\in X$, 
    there exists open neighbourhood $U\ni x$ such that there is an exact sequence with $I,J$ finite
    \begin{equation}
        \mathcal{O}_{U}^{\oplus J} \longrightarrow \mathcal{O}_{U}^{\oplus I} \longrightarrow \mathcal{F}\big{|}_{U} \longrightarrow 0
    \end{equation}
    \label{Proposition 1.9}
\end{proposition}
\begin{proof}
    "$\Rightarrow$": For $\mathcal{F}$ quasi-coherent and all $x\in X$, 
    there is affine open neighbourhood $U = \spec A\ni x$ such that $\mathcal{F}\big{|}_{U} \cong \widetilde{M}$ for some $A$-module $M$.
    Note that there is an exact sequence for some index sets $I,J$
    \begin{equation}
        A^{\oplus J} \longrightarrow A^{\oplus I} \longrightarrow M \longrightarrow 0
    \end{equation}
    By Proposition \ref{Proposition 1.6} (3), get exact sequence
    \begin{equation}
        \mathcal{O}_{U}^{\oplus J} \longrightarrow \mathcal{O}_{U}^{\oplus I} \longrightarrow \mathcal{F}\big{|}_{U} \longrightarrow 0
    \end{equation}
    \par
    "$\Leftarrow$": For all $x\in X$, there exists open neighbourhood $U\ni x$ such that there is an exact sequence
    \begin{equation}
        \mathcal{O}_{U}^{\oplus J} \longrightarrow \mathcal{O}_{U}^{\oplus I} \longrightarrow \mathcal{F}\big{|}_{U} \longrightarrow 0
    \end{equation}
    Can assume that $U$ is affine.
    By Proposition \ref{Proposition 1.9}, get exact sequence
    \begin{equation}
        \mathcal{O}_{U}(U)^{\oplus J} \longrightarrow \mathcal{O}_{U}(U)^{\oplus I} \longrightarrow \mathcal{F}\big{|}_{U}(U) \longrightarrow 0
    \end{equation}
    By Proposition \ref{Proposition 1.6}, get exact sequence
    \begin{equation}
        \mathcal{O}_{U}^{\oplus J} \longrightarrow \mathcal{O}_{U}^{\oplus I} \longrightarrow \widetilde{\mathcal{F}\big{|}_{U}(U)} \longrightarrow 0
    \end{equation}
    Thus $\mathcal{F}\big{|}_{U} \cong \widetilde{\mathcal{F}\big{|}_{U}(U)}$.
    By Theorem \ref{Theorem 1.1}, $\mathcal{F}$ is quasi-coherent.
    For coherent, the same argument would make sense.
\end{proof}
\begin{example}
    (1)Let $X$ be a scheme.
    Then locally free $\mathcal{O}_{X}$-modules are quasi-coherent. \\
    (2)Let $X$ be a noetherian scheme.
    Then locally free $\mathcal{O}_{X}$-modules of rank $< \infty$ are coherent. \\
    (3)Let $i: Y \longrightarrow X$ be a closed immersion with $X,Y$ noetherian.
    Then $i_{\ast}\mathcal{O}_{Y}$ is coherent on $X$. \\
    (4)Let $X$ be an integral noetherian scheme with function field $K$.
    Then constant sheaf $K_{X}$ is quasi-coherent but not coherent in general. \\
    (5)Let $X$ be a scheme, $U \subseteq X$ open subset with inclusion $j: U \longrightarrow X$, $\mathcal{F}$ sheaf on $U$.
    Define $j_{!}\mathcal{F}$ to be the sheafification of $V \longmapsto
    \left\{
        \begin{aligned}
            & \mathcal{F}(V) & \text{if } V \subseteq U \\
            & 0 & otherwise
        \end{aligned}
    \right.
    $.
    Then stalk $(j_{!}\mathcal{F})_{x} =
    \left\{
        \begin{aligned}
            & \mathcal{F}_{x} & \text{if } x\in U \\
            & 0 & otherwise
        \end{aligned}
    \right.
    $.
    Now let $X = \spec A$ be an affine scheme with $A$ integral domain, $U \subsetneq X$ nonempty open subset with inclusion $j: U \longrightarrow X$.
    Then $j_{!}\mathcal{O}_{U}$ is an $\mathcal{O}_{X}$-module but not quasi-coherent.
\end{example}
Now assume that $S$ is a graded ring.
Let $M = \oplus_{d\in \mathbb{Z}} M_{d}$ be a graded $C$-module.
Define $\widetilde{M}$ on $X = \proj(S)$ by the same process on $\mathcal{O}$ replacing $S$ by $M$.
In particular, $\widetilde{M}\big{|}_{D_{+}(f)} = \widetilde{M_{(f)}}$ and $\widetilde{M}_{\mathfrak{p}} = M_{(\mathfrak{p})}$ for $\mathfrak{p}\in X$.
Then $\widetilde{M}$ is quasi-coherent on $X$ and coherent if $X$ is noetherian and $M$ is finitely generated.
In addition, we should note that $\widetilde{M}$ doesn't determine $M$.
For instance, if $M = \oplus_{d \ge 0} M_{d}$ and $N = \oplus_{d \ge d_{0}} M_{d}$ for some $d_{0} > 0$, then $\widetilde{M} = \widetilde{N}$.
\begin{definition}[\textbf{\emph{Twisting}}]
    Let $S$ be a graded ring and $X = \proj(S)$, $\mathcal{F}$ an $\mathcal{O}_{X}$-module.
    Set $\mathcal{O}_{X}(n) = \widetilde{S(n)}$ where $S(n)$ is the graded $C$-module given by $S(n)_{d} = S_(n + d)$.
    Also set $\mathcal{F}(n) = \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{O}_{X}(n)$.
\end{definition}
\begin{proposition}
    Let $S$ be a graded ring and $X = \proj(S)$.
    Assume that $S$ is generated by $S_{1}$ as $S_{0}$-algebra.
    Then $\mathcal{O}_{X}$ is an invertible sheaf.
    In addition, For all graded $S$-module $M$, we have $\widetilde{M(n)} = \widetilde{M}(n)$.
    In particular, $\mathcal{O}_{X}(n) \otimes_{\mathcal{O}_{X}} \mathcal{O}_{X}(m) \cong \mathcal{O}_{X}(m + n)$.
    \label{Proposition 1.10}
\end{proposition}
\begin{proof}
    Since $S$ is generated by $S_{1}$ as $S_{0}$-algebra, $\{D_{+}(f)\}_{f\in S_{1}}$ cover $X$.
    Suffice to show for all $f\in S_{1}$, $S(n)_{(f)}$ is free of rank $1$ over $S_{(f)}$.
    Note that there is a canonical isomorphism $S(n)_{(f)} \longrightarrow S_{(f)}\quad s \longmapsto f^{-n}s$, done! 
\end{proof}
\begin{lemma}[\textbf{\emph{qcqs Lemma}}]
    Let $X$ be a scheme, $\mathcal{F}$ quasi-coherent sheaf on $X$, $\mathcal{L}$ invertible sheaf on $X$, $s\in \mathcal{L}(X)$.
    Assume that $X$ is either noetherian or quasi-compact and separated over $\spec(\mathbb{Z})$.
    Then \\
    (1)Let $f\in \mathcal{F}(X)$.
    If $f\big{|}_{X_{s}} = 0$, then there exists $n > 0$ such that $f \otimes s^{n} = 0$ in $(\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})(X)$,
    where $X_{s} = \{x\in X \big{|} s_{x}\mathcal{O}_{X, x} = \mathcal{L}_{x}\}$ is open and $\mathcal{L}^{n}$ denotes $\mathcal{L}^{\otimes n}$. \\
    (2)Let $g\in \mathcal{F}(X_{s})$.
    Then there exists $n_{0} > 0$ such that for all $n \ge n_{0}$,
    $g \otimes (s^{n}\big{|}_{X_{s}})$ extends to a section in $(\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})(X)$.
    \label{Lemma 1.2}
\end{lemma}
\begin{proof}
    Cover $X$ by finitely many affine open subsets $\{U_{i}\}$ such that $\mathcal{L}\big{|}_{U_{i}}$ is free and generated by $e_{i}\in \mathcal{L}(U_{i})$.
    Then $s_{i} = s\big{|}_{U_{i}} = h_{i}e_{i}$ for some $h_{i}\in \mathcal{O}_{X}(U_{i})$.
    Get $X_{s} \cap U_{i} = D(h_{i}) \subseteq U_{i}$.  
    \par
    (1): Note that $\mathcal{F}\big{|}_{U_{i}} \cong \widetilde{\mathcal{F}(U_{i})}$.
    Since $f\big{|}_{D(h_{i})}$, there exists $n > 0$ such that for all i, $f_{i} = f\big{|}_{U_{i}}$ satisfies that $h_{i}^{n}f_{i} = 0$ in $\mathcal{F}(U_{i})$.
    Thus $(f \otimes s)\big{|}_{U_{i}} = f_{i} \otimes s_{i}^{n} = h_{i}^{n}f_{i} \otimes e_{i}^{n} = 0$.
    As $U_{i}$ cover $X$, get $f \otimes s^{n} = 0$.
    \par
    (2): Set $g_{i} = g\big{|}_{D(h_{i})}$,
    Then there exists $m > 0$ such that for all $i$, there exists $g_{i}'\in \mathcal{F}(U_{i})$ such that $h_{i}^{m}g_{i} = g_{i}'$.
    Set $t_{i} = g_{i}' \otimes e_{i}^{m}\in (\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{m})(U_{i})$.
    Note that $t_{i}$ and $t_{j}$ coincide on $X_{s} \cap U_{i} \cap U_{j}$.
    Thus $(t_{i}\big{|}_{U_{i} \cap U_{j}} - t_{j}\big{|}_{U_{i} \cap U_{j}})\big{|}_{X_{s} \cap U_{i} \cap U_{j}}$.
    As $U_{i} \cap U_{j}$ is either noetherian or affine, by (1), there exists $p > 0$ such that $(t_{i}\big{|}_{U_{i} \cap U_{j}} - t_{j}\big{|}_{U_{i} \cap U_{j}}) \otimes s\big{|}_{U_{i} \cap U_{j}}^{p} = 0$ in $((\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{m})\big{|}_{U_{i} \cap U_{j}} \otimes_{\mathcal{O}_{U_{i} \cap U_{j}}} (\mathcal{L}\big{|}_{U_{i} \cap U_{j}})^{p})(U_{i} \cap U_{j})$.
    While $(\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{m})\big{|}_{U_{i} \cap U_{j}} \otimes_{\mathcal{O}_{U_{i} \cap U_{j}}} (\mathcal{L}\big{|}_{U_{i} \cap U_{j}})^{p} \cong (\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{m + p})\big{|}_{U_{i} \cap U_{j}}$, 
    get $t_{i} \otimes s_{i}^{p}$ and $t_{j} \otimes s_{j}^{p}$ coincide on $U_{i} \cap U_{j}$.
    Thus we can glue them to obtain $t\in (\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{m + p})(X)$ such that $t\big{|}_{X_{s}} = g \otimes (s\big{|}_{X_{s}}^{m + s})$.
    Take $n_{0} = m + p$, done!
\end{proof}
\begin{definition}
    Let $X$ be a scheme, $\mathcal{F}$ an $\mathcal{O}_{X}$-module.
    We say that $\mathcal{F}$ is generated by global sections (or say globally generated) if there exists a family of global sections $\{s_{i}\}$ such that for all $x\in X$,
    $\{(s_{i})_{x}\}$ generate $\mathcal{F}_{x}$.
\end{definition}
\begin{remark}
    Note that $\mathcal{F}$ is generated by global sections if and only if $\mathcal{F}$ is a quotient of a free $\mathcal{O}_{X}$-module.
\end{remark}
\begin{example}
    (1)Let $X = \mathbb{P}_{k}^{n}$ be projective $k$-scheme.
    Then $\mathcal{O}_{X}(-1)$ is not generated by global sections since there is no global sections at all. \\
    (2)Let $X = \spec A$ be an affine scheme.
    Then all quasi-coherent sheaves on $X$ are generated by global sections.
\end{example}
\begin{definition}
    Let $A$ be a ring and $X$ be a projective scheme over $A$ with commutative diagram
    \begin{equation}
        \begin{tikzcd}
            X \arrow[r, "i"] \arrow[dr] &
            \mathbb{P}_{A}^{d} \arrow[d] \\
            & \spec A
        \end{tikzcd}
    \end{equation}
    Set $\mathcal{O}_{X}(n) = i^{\ast}\mathcal{O}_{\mathbb{P}_{A}^{d}}(n)$.
    For $\mathcal{F}$ an $\mathcal{O}_{X}$-module, also set $\mathcal{F}(m) = \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{O}_{X}(n)$.
\end{definition}
\begin{lemma}[\textbf{\emph{Projection Formula for Affine Case}}]
    Let $f: X \longrightarrow Y$ be an affine morphism, $\mathcal{F}$ a quasi-coherent sheaf on $X$, $\mathcal{G}$ a quasi-coherent sheaf on $Y$.
    Then $f_{\ast}(\mathcal{F} \otimes_{\mathcal{O}_{X}} f^{\ast}\mathcal{G}) \cong f_{\ast}\mathcal{F} \otimes_{\mathcal{O}_{Y}} \mathcal{G}$.
    \label{Lemma 1.3}
\end{lemma}
\begin{proof}
    Can assume that $X = \spec(B)$, $Y = \spec A$, $\mathcal{F} = \widetilde{N}$ and $\widetilde{M}$.
    Then $f_{\ast}(\mathcal{F} \otimes_{\mathcal{O}_{X}} f^{\ast}\mathcal{G}) \cong \widetilde{P}$,
    where $P = N \otimes_{B} (M \otimes_{A} B)$ as $A$-module.
    On the other hand, $f_{\ast}\mathcal{F} \otimes \mathcal{G} \cong \widetilde{Q}$,
    where $Q = N \otimes_{A} M$ as $A$-module.
    As $P \cong Q$, done!
\end{proof}
\begin{theorem}[\textbf{\emph{Serre's Theorem}}]
    Let $A$ be a noetherian ring and $X$ be a projective scheme over $A$ with commutative diagram, 
    \begin{equation}
        \begin{tikzcd}
            X \arrow[r, "i"] \arrow[dr] &
            \mathbb{P}_{A}^{d} \arrow[d] \\
            & \spec A
        \end{tikzcd}
    \end{equation}
    Assume that $\mathcal{F}$ is a coherent sheaf on $X$.
    Then there exists $n_{0} > 0$ such that for all $n \ge n_{0}$, $\mathcal{F}(n)$ is generated by finitely many global sections.
    \label{Theorem 1.2}
\end{theorem}
\begin{proof}
    Since $i$ is a closed immersion, $i$ is finite so that $i_{\ast}\mathcal{F}$ is coherent.
    By Lemma \ref{Lemma 1.3}, $i_{\ast}(\mathcal{F}(n)) \cong (i_{\ast}\mathcal{F})(n)$.
    Thus global sections of $i_{\ast}(\mathcal{F}(n))$ are equal to global sections of $(i_{\ast}\mathcal{F})(n)$ and stalks of $i_{\ast}(\mathcal{F}(n))$ are equal to stalks of $(i_{\ast}\mathcal{F})(n)$.
    It suffices to prove for $X = \mathbb{P}_{A}^{d} = \proj(A[x_{0}, \cdots, x_{d}])$.
    \par
    Cover $X$ by $\{U_{i} = D_{+}(x_{i})\}$.
    Each $\mathcal{F}\big{|}_{U_{i}}$ is generated by finitely many sections $g_{ij}\in \mathcal{F}(U_{i})$.
    By Lemma \ref{Lemma 1.2}, there exists $n_{0} > 0$ such that $g_{ij} \otimes x_{i}^{n}$ extends to a global section for all $i,j$.
    Thus $\mathcal{F}(n)$ is generated by these extensions.
\end{proof}
\begin{corollary}
    Let $A$ be a noetherian ring and $X$ be a projective scheme over $A$ with commutative diagram, 
    \begin{equation}
        \begin{tikzcd}
            X \arrow[r, "i"] \arrow[dr] &
            \mathbb{P}_{A}^{d} \arrow[d] \\
            & \spec A
        \end{tikzcd}
    \end{equation}
    Assume that $\mathcal{F}$ is a coherent sheaf on $X$.
    Then there exists $m\in \mathbb{Z}$ and $r < \infty$ such that $\mathcal{F}$ is a quotient of $\mathcal{O}_{X}(m)^{\oplus r}$.
    \label{Corollary 1.1}
\end{corollary}
\begin{reason}
    Since $\mathcal{F}(n)$ is generated bv global sections for large enough $n$,
    $\mathcal{F}(n)$ is quotient of $\mathcal{O}_{X}^{\oplus I}$ with finite index set.
    Tensor by $\mathcal{O}_{X}(-n)$, done!
\end{reason}

\subsection{Vector bundles}
\label{subsection:Vector_Bundles_Vector_bundles}

Let $X$ be an algebraic variety which we mean a separated scheme of finite type over $\mathbb{C}$.
And all morphisms mentioned are morphisms of varieties.
\begin{definition}
    A complex linear fibration over $X$ is a surjection $p: E \twoheadrightarrow X$ from variety $E$ such that for all $x\in X$, 
    the fiber $E_{x}$ is an affine space.
    In convention, we call $E$ the total space and $X$ the base variety.
\end{definition}
\begin{example}
    We call $X \times \mathbb{A}_{\mathbb{C}}^{r} \rightarrow X$ the trivial fibration of rank $r$.
\end{example}
\begin{lemma}
    Given a linear fibration $p: E \rightarrow X$, for any open subset $U \subseteq X$,
    the restriction $p^{-1}(U) \rightarrow U$ is also a linear fibration.
    Denote $E\big{|}_{U} = p^{-1}(U)$.
    \label{Lemma 1.4}
\end{lemma}
\begin{definition}
    Given two linear fibrations $E \overset{p}{\rightarrow} X$ and $F \overset{q}{\rightarrow} X$,
    a morphism $f: E \rightarrow F$ is said to be a morphism of linear fibrations if the following diagram commutes
    \begin{equation}
        \begin{tikzcd}
            E \arrow[rr, "f"] \arrow[dr, "p" swap] &&
            F \arrow[dl, "q"] \\
            & X &
        \end{tikzcd}
    \end{equation}
    and for all $x\in X$, $E_{x} \overset{f_{x}}{\rightarrow} F_{x}$ is a linear transformation.
\end{definition}
\begin{definition}
    An algebraic vector bundle of rank $r$ on $X$ is a linear fibration $E \overset{p}{\rightarrow} X$ which is locally trivial i.e. for all $x\in X$,
    there is an open neighbourhood $U$ of $x$ and isomorphism of linear fibrations $\varphi_{U}$ such that the following diagram commutes
    \begin{equation}
        \begin{tikzcd}
            E\big{|}_{U} \arrow[rr, "\varphi_{U}"] \arrow[dr, "p" swap] &&
            U \times \mathbb{A}_{\mathbb{C}}^{r} \arrow[dl] \\
            & U &
        \end{tikzcd}
    \end{equation}
    where $\varphi_{U}$ are called the local charts or local trivialization.
    \par
    And for two such $U_{i}$ and $U_{j}$ with local charts $\varphi_{i}$ and $\varphi_{j}$,
    there is an invertible matrix $g_{ij}$ with entries regular functions on $U_{ij}$, called transition function,
    satisfying that $g_{ii} = I_{r}$, $g_{ij} \cdot g_{jk} = g_{ik}$ and for all affine open subset $W \subseteq U_{ij}$,
    $\varphi_{i} \circ \varphi_{j}^{-1}\big{|}_{W}$ is linear transformation defined by $g_{ij}\big{|}_{W}$.
    Equivalently, $g_{ij}$ would correspond to a morphism $\widetilde{g}_{ij}: U_{ij} \rightarrow \generallineargroup{r}{\mathcal{O}_{X}(U_{ij})}$.
\end{definition}
\begin{lemma}
    Given data $\{g_{ij}\}$ satisfies that $g_{ii} = I_{r}$ and $g_{ij} \cdot g_{jk} = g_{ik}$, we can recover a vector bundle.
    \label{Lemma 1.5}
\end{lemma}
\begin{proof}
    Construct $E$ by gluing up $U_{i} \times \mathbb{A}_{\mathbb{C}}^{r}$ along $U_{ij} \times \mathbb{A}_{\mathbb{C}}^{r} \overset{\varphi_{ij}}{\rightarrow} U_{ij} \times \mathbb{A}_{\mathbb{C}}^{r}$ defined by $g_{ij}$.
\end{proof}
\begin{definition}
    Let $E, F$ be two vector bundles on $X$ of rank $r$ and $s$ respectively.
    We say a morphism $f: E \rightarrow F$ of linear fibrations is a morphism of vector bundles if there is a $r \times s$ matrix $g_{U}$ with entries regular functions on $U$ such that for all affine open subset $W \subseteq U$, 
    restriction of the following morphism to $W$ is linear transformation defined by $g_{U}\big{|}_{W}$
    \begin{equation}
        U \times \mathbb{A}_{\mathbb{C}}^{r} \overset{\varphi_{U}^{-1}}{\rightarrow} E\big{|}_{U} \overset{f\big{|}_{U}}{\rightarrow} F\big{|}_{U} \overset{\psi_{U}}{\rightarrow} U \times \mathbb{A}_{\mathbb{C}}^{s}
    \end{equation}
    where $\varphi_{U}$ and $\psi_{U}$ are local charts.
    Equivalently, $g_{U}$ would correspond to a morphism $\widetilde{g}_{U}: U \rightarrow \generallineargroup{r}{\mathcal{O}_{X}(U)}$.
\end{definition}
\begin{remark}
    With Lemma \ref{Lemma 1.5}, we can easily define $E \oplus F$, $E \otimes F$, $\sheafhom(E, F)$, $E^{\vee}$, $\wedge^{k} E$ and $S^{k} E$.
\end{remark}
\begin{proposition}
    Let $f: E \rightarrow F$ be a morphism of vector bundles.
    Assume that for $x_{0}\in X$, $f_{x_{0}}: E_{x_{0}} \rightarrow F_{x_{0}}$ is invertible.
    Then there exists an open neighbourhood $U_{0}$ of $x_{0}$ such that $f\big{|}_{U}: E\big{|}_{U} \rightarrow F\big{|}_{U}$ is an isomorphism.
    \label{Proposition 1.11}
\end{proposition}
\begin{proof}
    Assume $x_{0}\in U$ with local charts $\varphi_{U}: E\big{|}_{U} \rightarrow U \times \mathbb{A}_{\mathbb{C}}^{r}$ and $\psi_{U}: F\big{|}_{U} \rightarrow \mathbb{A}_{\mathbb{C}}^{s}$.
    By definition, there is a matrix $g_{U}$ and $f_{x_{0}}$ is defined by $g_{U}(x_{0})$.
    This immediately comes from the fact that there exists an open neighbourhood $U_{0} \subseteq U$ of $x_{0}$ such that $g_{U}\big{|}_{U_{0}}$ is invertible.
\end{proof}
\begin{definition}
    Let $E$ be a vector bundle of rank $r$ on $X$.
    A subbundle of rank $m$ of $E$ is a subvariety $F \subseteq E$ such that fiber $F_{x}$ is an $m$-dimensional affine linear subspace of $E_{x}$ and the induced fibration $p\big{|}_{F}: F \rightarrow X$ is locally trivial.
\end{definition}
\begin{example}
    Let $X = \mathbb{P}_{\mathbb{C}}^{n}$ be $n$-dimensional projective space with homogeneous coordinate $x_{0}, \cdots, x_{n}$.
    Consider the subvariety $\Sigma := V(x_{i}y_{j} - x_{j}y_{i})$ of $X \times \mathbb{A}_{\mathbb{C}}^{n + 1}$,
    where $y_{0}, \cdots, y_{n}$ are coordinate of $\mathbb{A}_{\mathbb{C}}^{n + 1}$.
    Then the fiber is a $1$-dimensional affine space and hence $\Sigma$ is a subbundle of rank $1$ of the trivial bundle, denoted by $\mathcal{O}(-1)$.
\end{example}
\begin{proposition}
    Let $F \subseteq E$ be a subbundle of rank $m$.
    Then there exists unique vector bundle structure on $E/F$ satisfying the universal property that any map of vector bundles $E \rightarrow G$ vanishing over $F$ would factor through $E/F$ uniquely.
    \label{Proposition 1.12}
\end{proposition}
\begin{proof}
    Firstly cover $X$ with affine open subsets trivializing $F$ and $E$, we may assume that $X = \spec A$, $E = \mathbb{A}_{A}^{n}$ and $F = \mathbb{A}_{A}^{m}$.
    Since $F \subseteq E$ is a subbundle, by definition, for all $x\in X$,
    $E_{x} = \mathbb{A}_{k(x)}^{n}$ and $F_{x} = \mathbb{A}_{k(x)}^{m}$ with coordinates $x_{1}, \cdots, x_{n}$ and $y_{1}, \cdots, y_{m}$ respectively,
    satisfying that $y_{i}$ can be linearly represented by $x_{i}$.
    \par
    It is clear that these relations still hold over a neighbourhood $U = D(f)$ of $x$.
    Then we extend $y_{i}$ to a basis $y_{1}, \cdots, y_{m}, z_{1}, \cdots, z_{n - m}$ and hence $\spec A_{f}[x_{1}, \cdots, x_{n}]/(y_{1}, \cdots, y_{m}) \cong \spec A_{f}[z_{1}, \cdots, z_{n - m}]$ is a linear subspace.
    For different $D(f)$ and $D(g)$, since $z_{1}, \cdots, z_{n - m}$ and $z_{1}', \cdots, z_{n - m}'$ span same linear subspace,
    there is an invertible transformation matrix $M\in \matrices{n - m}{A_{fg}}$ i.e. the transition function.
    Thus we defines a vector bundle structure on $E/F$.
    \par
    Now given a map of vector bundles $E \rightarrow G$ vanishing over $F$.
    Still assume that $X = \spec A$ trivializing all those bundles.
    Then $E \rightarrow G$ corresponds to a linear transformation $\varphi: A[w_{1}, \cdots, w_{r}] \rightarrow A[x_{1}, \cdots, x_{n}]$,
    which is defined by an $n \times r$ matrix with entries in $A$.
    By assumption, we know $y_{i}$ are not in the image of $\varphi$ and hence $\im \varphi$ lies in the subspace spanned by $z_{i}$.
    Thus $\varphi$ factors a canonical map $A[w_{1}, \cdots, w_{r}] \rightarrow A[z_{1}, \cdots, z_{n - m}]$.
    Finally, by universal property, we know the vector bundle structure on $E/F$ is also unique.
\end{proof}
\begin{proposition}[\textbf{\emph{Rigidity Property}}]
    Let $f: E \rightarrow F$ be a map of vector bundles.
    Suppose that rank of fiber morphisms $f_{x}$ is constant as $x$ varies over $X$.
    Then $\ker f$ and $\im f$ are subbundles of $E$ and $F$ respectively.
    \label{Proposition 1.13}
\end{proposition}
\begin{proof}
    Here we only show $\ker f$ is a subbundle of $E$ and similar argument makes sense for $\im f$.
    We may assume that $X = \spec A$ trivializing both $E$ and $F$.
    Now $f$ corresponds to a linear transformation $\varphi: A[y_{1}, \cdots, y_{m}] \rightarrow A[x_{1}, \cdots, x_{n}]$ defined by an $n \times m$ matrix $M$ with entries in $A$.
    \par
    Since the rank of fiber morphism is constant, we know both the dimensions of $\im \varphi_{x}$ are constant, denoted by $n - r$.
    Then we may choose $y_{1}, \cdots, y_{r}$ spanning the complementary subspace of $\im \varphi_{x}$, which can be linearly represented by $x_{i}$.
    And these relation still hold over an neighbourhood $U = D(f)$ of $x$.
    For different $D(f)$ and $D(g)$, since both $y_{1}, \cdots, y_{r}$ and $y_{1}', \cdots, y_{r}'$ span complementary subspace of $\im \varphi_{fg}$,
    there is an invertible transformation matrix $M\in \matrices{r}{A_{fg}}$ i.e. the transition function.
    Thus we give a subbundle structure on $\ker f$.
\end{proof}
\begin{remark}
    Though proof for $\im f$ follows by similar argument, there is still a little tricky thing in that case.
    When we talk about $\ker f_{x}$, it is clear the points living outside $\im \varphi_{x}$.
    But when we talk about $\im f_{x}$, what are they?
    As $X$ is locally noetherian, by a proposition in Some Useful Results, we know they are just the points living in coimage of $\varphi_{x}$.
    \par
    In addition, since this note is translated by me from language of varieties to language of schemes,
    there must be some ambiguity about the terminology.
    For example, here by $\ker f$, we possibly mean the subset of points whoes image under $f$ are same to image of the origin.
\end{remark}
\begin{corollary}
    Let $f: E \rightarrow F$ be a map of vector bundles.
    When $f$ is surjective, $\ker f$ is a subbundle of $E$.
    And when $f$ is injective, $\im f$ is a subbundle of $F$.
    \label{Corollary 1.2}
\end{corollary}
\begin{reason}
    When $f$ is surjective, as remark above, we know $\ker \varphi = 0$ so that rank of $f_{x}$ is constant.
    When $f$ is injective, as proof above, we know $\im \varphi = k[x_{1}, \cdots, x_{n}]$ so that rank of $f_{x}$ is constant.
\end{reason}
\begin{definition}
    Let $p: E \rightarrow X$ be a vector bundle on $X$ of rank $r$.
    A (regular) section of $E$ over open subset $U \subseteq X$ is a morphism $s: U \rightarrow E$ such that $(p \circ s)\big{|}_{U} = \identity_{U}$.
    Denote $\Gamma(U, E) = \{\text{regular sections of $E$ over $U$}\}$.
\end{definition}
\begin{lemma}
    Let $p: E \rightarrow X$ be a vector bundle on $X$ of rank $r$.
    Then $\Gamma(U, E)$ naturally admits an $\mathcal{O}(U)$-module structure
    \begin{equation}
        \mathcal{O}(U) \times \Gamma(U, E) \longrightarrow \Gamma(U, E)
    \end{equation}
    Moreover, $\mathcal{O}_{X}(E)(U) = \Gamma(U, E)$ gives a locally free sheaf $\mathcal{O}_{X}(E)$ of rank $r$.
    \label{Lemma 1.6}
\end{lemma}
\begin{proof}
    For $\alpha\in \mathcal{O}(U)$ and section $s: U \rightarrow E$, locally $s$ is defined by a homomorphism $\varphi: A[x_{1}, \cdots, x_{r}] \rightarrow A$.
    Define $\alpha \cdot s$ by gluing up $\alpha \cdot \varphi: x_{i} \mapsto \alpha \cdot \varphi(x_{i})$.
    In particular, locally $\Gamma(U, E) \cong A^{\oplus r}$ hence $\mathcal{O}_{X}(E)$ is a locally free sheaf of rank $r$. 
\end{proof}
\begin{proposition}
    Let $\mathcal{C}$ be the category of locally free sheaves of finite rank on $X$.
    There is a functor $\theta: \vectorbundle_{X} \rightarrow \mathcal{C}$ sending $E$ to $\mathcal{O}_{X}(E)$ and $E \rightarrow F$ to $\{\Gamma(U, E) \rightarrow \Gamma(U, F)\}$,
    which is an equivalence of category.
    \label{Proposition 1.14}
\end{proposition}
\begin{proof}
    First to prove $\theta$ fully faithful i.e. $\hom_{\vectorbundle_{X}}(E, F) \rightarrow \hom_{\mathcal{O}_{X}}(\mathcal{O}_{X}(E), \mathcal{O}_{X}(F))$ is bijection for all $E, F$.
    We may assume that $X = \spec A$ and $E, F$ are both trivial.
    Then $f: \mathbb{A}_{A}^{n} \rightarrow \mathbb{A}_{A}^{m}$ corresponds to a matrix $M\in \matrices{n \times m}{A}$.
    Also, $(s: U \rightarrow E) \rightarrow (f \circ s: U \rightarrow F)$ also corresponds to such a matrix.
    Hence the bijection is clear.
    \par
    Next to prover $\theta$ dense (or say essentially surjective) i.e. given $\mathcal{E}\in \mathcal{C}$, there exists $E\in \vectorbundle_{X}$ with isomorphism $\mathcal{O}_{X}(E) \overset{\sim}{\rightarrow} \mathcal{E}$.
    Assume $U_{i} = \spec A_{i}$ is an affine cover of $X$ trivializing $\mathcal{E}$.
    Denote the trivialization $\varphi_{i}: \mathcal{E}\big{|}_{U_{i}} \rightarrow \mathbb{A}_{A_{i}}^{n}$.
    Consider the transition functions $g_{ij} = \varphi_{i} \circ \varphi_{j}^{-1}\big{|}_{U_{ij}}$.
    Then thoes transition functions give a vector bundle $E$.
    \par
    Define $\psi_{i}: \mathcal{O}_{X}(E)(U_{i}) = \Gamma(U_{i}, E) \rightarrow \mathcal{E}\big{|}_{U_{i}}$ sending $s: U_{i} \rightarrow \mathbb{A}_{U_{i}}^{n}$ to $\varphi_{i}^{-1}(v_{s})$,
    where $v_{s}$ is the vector defining $s$.
    Then 
    \begin{equation}
        \psi_{i}\big{|}_{U_{ij}}(s\big{|}_{U_{ij}}) = \varphi_{i}^{-1}(v_{s}) = \varphi_{i}^{-1}(g_{ij}v_{s}') = \varphi_{i}^{-1} \circ \varphi_{i} \circ \varphi_{j}^{-1}(v_{s}') = \varphi_{j}^{-1}(v_{s}') = \psi_{j}\big{|}_{U_{ij}}(s\big{|}_{U_{ij}})
    \end{equation}
    Hence $\psi_{i}$ glue up and get our desired isomorphism.
\end{proof}

\subsection{Bundles associated to a representation}
\label{subsection:Vector_Bundles_Bundles_associated_to_a_representation}

\begin{lemma}
    Let $f: Y \rightarrow X$ be a morphism, $p: E \rightarrow X$ vector bundle of rank $r$ on $X$.
    Consider the fibered product $F = Y \times_{X} E$.
    Then the first projection $q: F \rightarrow Y$ gives a bundle on $Y$ of rank $r$ and $\mathcal{O}_{Y}(F) = f^{\ast}\mathcal{O}_{X}(E)$.
    \label{Lemma 1.7}
\end{lemma}
\begin{proof}
    Locally we have trivializations $\varphi_{i}: E\big{|}_{U_{i}} \rightarrow U_{i} \times \mathbb{A}_{\mathbb{{C}}}^{r}$ and transition functions $g_{ij}: U_{ij} \times \mathbb{A}_{\mathbb{{C}}}^{r} \rightarrow U_{ij} \times \mathbb{A}_{\mathbb{{C}}}^{r}$ satisfying cocycle condition.
    Then after base change we get $\widetilde{\varphi}_{i}: F\big{|}_{V_{i}} \rightarrow V_{i} \times \mathbb{A}_{\mathbb{{C}}}^{r}$ and $\widetilde{g}_{ij}: U_{ij} \times \mathbb{A}_{\mathbb{{C}}}^{r} \rightarrow U_{ij} \times \mathbb{A}_{\mathbb{{C}}}^{r}$ still satisfying cocycle condition.
    Hence $q: F \rightarrow Y$ defines a bundle on $Y$ of rank $r$.
    \par
    Now for all open subset $V \subseteq Y$, define $\sigma(V): f^{\ast}\mathcal{O}_{X}(E)(V) \rightarrow \mathcal{O}_{Y}(F)(V)$ sending $(U, s) \otimes 1$ to $\widetilde{s}\big{|}_{V}$,
    where $\widetilde{s}: f^{-1}(U) \rightarrow F$ is the pull back of $s: U \rightarrow E$.
    For all $y\in Y$, want to show that $\sigma_{y}: \mathcal{O}_{X}(E)_{f(y)} \otimes_{\mathcal{O}_{X, f(y)}} \mathcal{O}_{Y, y} \rightarrow \mathcal{O}_{Y}(F)_{y}$ is isomorphism.
    \par
    For injectivity, if $\sum_{i = 1}^{r} (U, s_{i}) \otimes b_{i}\in \ker \sigma_{y}$,
    then locally we get $\sum_{i = 1}^{r} b_{i} \cdot f^{\sharp} \circ s_{i}^{\sharp}(x_{j}) = 0$ for all $1 \le j \le r$,
    so that also $\sum_{i = 1}^{r} (s_{i}^{\sharp}(x_{1}), \cdots, s_{i}^{\sharp}(x_{r})) \otimes b_{i} = 1 \otimes (\sum_{i = 1}^{r} b_{i} \cdot f^{\sharp} \circ s_{i}^{\sharp}(x_{1}), \cdots, \sum_{i = 1}^{r} b_{i} \cdot f^{\sharp} \circ s_{i}^{\sharp}(x_{r})) = 0$.
    Then $(U, s) = \oplus_{i = 1}^{r} a_{i} \otimes 1 = 0$.
    For surjectivity, given $(b_{1}, \cdots, b_{r})\in B^{\oplus r}$,
    clearly it is the image of $\sum_{i = 1}^{r} (U, s_{i}) \otimes b_{i}$ where $s_{i}$ is defined by $e_{i}\in A^{\oplus r}$.
\end{proof}
Let $p: E \rightarrow X$ be a vector bundle of rank $r$.
To avoid ambiguity, we denote the general linear group by $G_{r}$ and the group variety by $\generallineargroup{r}{\mathbb{C}}$,
which is the open subset $D(\det)$ of $\mathbb{A}_{\mathbb{C}}^{r^{2}}$.
Consider the variety $R = X \times \generallineargroup{r}{\mathbb{C}}$.
We have a group action of $G_{r}$ on $R$ defined locally as following, for $M = (a_{ij})$
\begin{equation}
    \begin{split}
        \identity \times (\circ M^{-1}): A \times \generallineargroup{r}{\mathbb{C}} \rightarrow A \times \generallineargroup{r}{\mathbb{C}}
    \end{split}
\end{equation}
where $\circ M^{-1}$ corresponds to the homomorphism defined by $(x_{ij}) \mapsto (\sum_{k} x_{ik}a_{kj})$.
Then $R/G_{r} = X$ and the orbits can be identified with the fibers of $R \rightarrow X$.
In addition, each matirx $M$ gives a morphism $\mathbb{A}_{\mathbb{C}}^{r} \rightarrow E\big{|}_{U}$ satisfying that composition with trivialization $\varphi_{U}$ is a linear transformation defined by $M$.
Then it is natural to consider transition function $g_{ij}$ which gives a $\generallineargroup{r}{\mathbb{C}}$-bundle on $X$, denoted by $\framebundle (E)$, the frame bundle of $E$.
And there is an group action of $G_{r}$ on $R \times \mathbb{A}_{\mathbb{C}}^{r}$ defined locally as following, for $M = (a_{ij})$
\begin{equation}
    \begin{split}
        \identity \times (\circ M^{-1}) \times M: A \times \generallineargroup{r}{\mathbb{C}} \times \mathbb{A}_{\mathbb{C}}^{r} \rightarrow A \times \generallineargroup{r}{\mathbb{C}} \times \mathbb{A}_{\mathbb{C}}^{r}
    \end{split}
\end{equation}
where $M$ corresponds to the linear transformation defined by $M$.
Consider $R \times \generallineargroup{r}{\mathbb{C}}/G_{r}$.
It is clear that $A[x_{ij}]_{(\det)}[y_{k}]^{G_{r}} = A[\sum_{k = 1}^{r} x_{ik}y_{k}]$ and hence the quotient scheme is isomorphic to $\mathbb{A}_{\mathbb{C}}^{r}$.
With transition functions $g_{ij}$, gluing up we get original $E$.  
\par
Now given a representation $\psi: \generallineargroup{r}{\mathbb{C}} \rightarrow \generallineargroup{m}{\mathbb{C}}$,
which is in fact a morphism of group schemes,
consider the group action of $G_{r}$ on $R \times \mathbb{A}_{\mathbb{C}}^{m}$ defined locally as following, for $M = (a_{ij})$
\begin{equation}
    \begin{split}
        \identity \times (\circ M^{-1}) \times \psi(M): A \times \generallineargroup{r}{\mathbb{C}} \times \mathbb{A}_{\mathbb{C}}^{m} \rightarrow A \times \generallineargroup{r}{\mathbb{C}} \times \mathbb{A}_{\mathbb{C}}^{m}
    \end{split}
\end{equation}
Since the representabtion corresponds to a homomorphism $A[y_{ij}] \rightarrow A[x_{ij}]$,
similarly the invariant subring is generated by $\psi(x_{ij})(y_{k})$,
where the $(i, j)$-entry of $\psi(x_{ij})$ is the image of $y_{ij}$ in $A[x_{ij}]$.
Then locally the quotient scheme is isomorphic to $\mathbb{A}_{A}^{m}$ with natural transition functions $\psi(g_{ij})$.
These information give a vector bundle $E_{\psi}$ of rank $m$ on $X$, called the bundle associated to representation $\psi$.
\begin{remark}
    The idea of frame bundle also comes from moduli thery.
    Consider functor $\mathcal{F}: \scheme_{X} \rightarrow \sets$ defined as following
    \begin{equation}
        (f: T \rightarrow X) \longmapsto \{f^{\ast}\mathcal{O}(E) \overset{\sim}{\rightarrow} \mathcal{O}_{T}^{r}\}
    \end{equation}
    And in fact this functor is representable by frame bundle above.
\end{remark}

\section{Sheaf Cohomology}
\label{section:Sheaf_Cohomology}

\subsection{Cohomology group}
\label{subsection:Sheaf_Cohomology_Cohomology_group}

There are lots of abelian categories in Algebraic Geometry.
\begin{example}
    (1)$\abeliangroups$ is the category of abelian groups. \\
    (2)$\module_{A}$ is the category of $A$-modules. \\
    (3)$\abeliangroups (X)$ is the category of sheaves of abelian groups on a topological space $X$. \\
    (4)$\module (\mathcal{O}_{X})$ is the category of $\mathcal{O}_{X}$-modules on a ringed space $(X, \mathcal{O}_{X})$. \\
    (5)$\quasicoherent (X)$ is the category of quasi-coherent sheaves on a scheme $X$. \\
    (6)$\coherent (X)$ is the category of coherent sheaves on a noetherian scheme $X$.
\end{example}
There are some special functors in Algebraic Geometry.
\begin{example}
    (1)$\hom_{\mathcal{C}}(A, \cdot): \mathcal{C} \longrightarrow \abeliangroups$ is left exact covariant functor. \\
    (2)$\hom_{\mathcal{C}}(\cdot, A): \mathcal{C} \longrightarrow \abeliangroups$ is left exact contravariant functor. \\
    (3)$\Gamma(X, \cdot): \abeliangroups (X) \longrightarrow \abeliangroups$ is left exact covariant functor. \\
    (4)$M \otimes_{A} \cdot: \module_{A} \longrightarrow \module_{A}$ is right exact covariant functor.
    In particular, $M \otimes_{A} \cdot$ is exact if and only if $M$ is flat $A$-module. 
\end{example}
\begin{definition}
    Let $\mathcal{C}$ be a category with enough injective objects, $\mathcal{F}$ a left exact covariant functor, $J\in \mathcal{C}$.
    We say that $J$ is acyclic for the functor $\mathcal{F}$ (or say $\mathcal{F}$-acyclic) if $R^{i}\mathcal{F}(J) = 0$ for all $i > 0$.
\end{definition}
\begin{proposition}
    Let $\mathcal{C}$ be a category with enough injective objects, $\mathcal{F}$ a left exact covariant functor, $A\in \mathcal{C}$.
    Assume that there is an $\mathcal{F}$-acyclic resolution $J^{\ast}$ of $A$ i.e. $0 \longrightarrow A \longrightarrow J_{0} \longrightarrow J_{1} \longrightarrow \cdots$ exact with each $J_{i}$ $\mathcal{F}$-acyclic.
    Then $R^{i}\mathcal{F}(A) \cong H^{i}(\mathcal{F}(J^{\ast}))$.
    \label{Proposition 2.1}
\end{proposition}
\begin{proposition}
    Let $(X, \mathcal{O}_{X})$ be a ringed space.
    Then $\module (\mathcal{O}_{X})$ has enough injective objects.
    In particular, $\abeliangroups (X)$ has enough injective objects if viewing X as $(X, \mathbb{Z}_{X})$ ringed space, where $\mathbb{Z}_{X}$ is the constant sheaf.
    \label{Proposition 2.2}
\end{proposition}
\begin{proof}
    Let $\mathcal{F}$ be an $\mathcal{O}_{X}$-module.
    For all $x\in X$, can embed $\mathcal{F}_{x}$ in an injective $\mathcal{O}_{X, x}$-module $I_{x}$ since $\module_{A}$ has enough injective objects for all ring $A$.
    View $I_{x}$ as a sheaf on $\{x\}$.
    Set $\mathcal{I} = \prod_{x\in X} j_{\ast}I_{X}$ where $j: \{x\} \longrightarrow X$ is inclusion.
    For all $\mathcal{G}$ $\mathcal{O}_{X}$-module, we have $\hom_{\mathcal{O}_{X}}(\mathcal{G}, \mathcal{I}) = \prod_{x\in X} \hom_{\mathcal{O}_{X}}(\mathcal{G}, j_{\ast}I_{x}) = \prod_{x\in X} \hom_{\mathcal{O}_{X, x}}(\mathcal{G}_{x}, I_{x})$.
    With $\mathcal{F}_{x} \hookrightarrow I_{x}$, get a monomorphism $\mathcal{F} \longrightarrow \mathcal{I}$ with $\mathcal{I}$ injective.
\end{proof}
\begin{definition}[\textbf{\emph{Sheaf Cohomology}}]
    Let $X$ be a topological space, $\Gamma(X, \cdot): \abeliangroups (X) \longrightarrow \abeliangroups$.
    Define the cohomology functor $H^{i}(X, \cdot) = R^{i}\Gamma(X, \cdot)$.
    For $\mathcal{F}\in \abeliangroups (X)$, we call $H^{i}(X, \mathcal{F})$ the ith cohomology group of $\mathcal{F}$.
\end{definition}
\begin{definition}
    Let $X$ be a topological space, $\mathcal{F}\in \abeliangroups (X)$.
    We say that $\mathcal{F}$ is flasque if for all $V \subseteq U$ inclusion of open subsets,
    the restriction map $\mathcal{F}(U) \longrightarrow \mathcal{F}(V)$ is surjective.
\end{definition}
\begin{proposition}
    (1)Direct products of flasque sheaves are flasque. \\
    (2)Direct image of flasque sheaves are flasque. \\
    (3)quotient of flasque sheaves by flasque sheaves are flasque. \\
    (4)If $0 \longrightarrow \mathcal{F} \longrightarrow \mathcal{G} \longrightarrow \mathcal{H} \longrightarrow 0$ is exact with $\mathcal{F}$ flasque,
    then $0 \longrightarrow \mathcal{F}(U) \longrightarrow \mathcal{G}(U) \longrightarrow \mathcal{H}(U) \longrightarrow 0$ is exact for all open subset $U \subseteq X$.
    \label{Proposition 2.3}
\end{proposition}
\begin{proposition}
    Let $(X, \mathcal{O}_{X})$ be a ringed space.
    Then every injective $\mathcal{O}_{X}$-module is flasque.
    \vspace{-\baselineskip} % 减少一行间距
    \label{Proposition 2.4}
\end{proposition}
\begin{proof}
    Consider $U \subseteq X$ is an inclusion of open subsets.
    Set $\mathcal{G}_{U} = j_{!}\mathcal{O}_{U}$.
    Let $\mathcal{F}$ be an injective $\mathcal{O}_{X}$-module, $V \subseteq U$ open subset.
    Then the natural morphism $\mathcal{G}_{V} \longrightarrow \mathcal{G}_{U}$ is monic so that $0 \longrightarrow \mathcal{G}_{V} \longrightarrow \mathcal{G}_{U}$ is exact.
    Since $\mathcal{F}$ is injective, get $\hom_{\mathcal{O}_{X}}(\mathcal{G}_{U}, \mathcal{F}) \longrightarrow \hom_{\mathcal{O}_{X}}(\mathcal{G}_{V}, \mathcal{F}) \longrightarrow 0$ exact.
    Note that $\hom_{\mathcal{O}_{X}}(\mathcal{G}_{U}, \mathcal{F})\big{|}_{U} = \hom_{\mathcal{O}_{U}}(\mathcal{O}_{U}, \mathcal{F}\big{|}_{U}) = \mathcal{F}(U)$.
    Thus $\mathcal{F}(U) \longrightarrow \mathcal{F}(V) \longrightarrow 0$ is exact so that $\mathcal{F}$ is flasque.
\end{proof}
\begin{corollary}
    Let $X$ be a topological space.
    Then every injective object in $\abeliangroups (X)$ is flasque by viewing $X$ as ringed space $(X, \mathbb{Z}_{X})$ where $\mathbb{Z}_{X}$ is the constant sheaf.
    \label{Corollary 2.1}
\end{corollary}
\begin{proposition}
    Let $X$ be a topological space.
    Then every flasque sheaf on $X$ is acyclic for the functor $\Gamma(X, \cdot)$.
    \label{Proposition 2.5}
\end{proposition}
\begin{proof}
    Let $\mathcal{F}$ be a flasque sheaf on $X$.
    Consider exact sequence $0 \longrightarrow \mathcal{F} \longrightarrow \mathcal{I} \longrightarrow \mathcal{G} \longrightarrow 0$ where $\mathcal{I}$ is an injective object in $\abeliangroups (X)$.
    By Corollary \ref{Corollary 2.1}, $\mathcal{I}$ is flasque.
    Thus $\mathcal{G}$ is flasque since it is quotient of flasque sheaf by flasque sheaf.
    Take the long exact sequence $0 \longrightarrow \mathcal{F}(X) \longrightarrow \mathcal{I}(X) \longrightarrow \mathcal{G}(X) \longrightarrow H^{1}(X, \mathcal{F}) \longrightarrow H^{1}(X, \mathcal{I}) \longrightarrow \cdots$.
    While $\mathcal{F}$ is flasque, we have $0 \longrightarrow \mathcal{F}(X) \longrightarrow \mathcal{I}(X) \longrightarrow \mathcal{G}(X) \longrightarrow 0$ is exact.
    Also, as $\mathcal{I}$ is injective, $H^{i}(X, \mathcal{I}) = 0$ for all $i > 0$.
    Thus $H^{i}(X, \mathcal{F}) = 0$ for all $i > 0$ so that $\mathcal{F}$ is acyclic for the functor $\Gamma(X, \cdot)$. 
\end{proof}
\begin{corollary}
    Let $(X, \mathcal{O}_{X})$ be a ringed space.
    Then the right derived functor of $\Gamma(X, \cdot): \module (\mathcal{O}_{X}) \longrightarrow \abeliangroups$ coincide with $H^{i}(X, \cdot)$.
    \label{Corollary 2.2}
\end{corollary}
\begin{reason}
    Take injective resolution in $\module (\mathcal{O}_{X})$.
    By Proposition \ref{Proposition 2.4} and Proposition \ref{Proposition 2.5}, it is a $\Gamma(X, \cdot)$-acyclic resolution.
    Thus by Proposition \ref{Proposition 2.1}, the two right derived functors coincide.
\end{reason}
\begin{corollary}
    Let $X$ be a topological space, $Y \subseteq X$ closed subset, $i: Y \longrightarrow X$ inclusion.
    Then for all $\mathcal{F}\in Ab(Y)$, we have $H^{i}(Y, \mathcal{F}) \cong H^{i}(X, j_{\ast}\mathcal{F})$.
    \label{Corollary 2.3}
\end{corollary}
\begin{reason}
    Take injective resolution $J^{\ast}$ of $\mathcal{F}$ in $\abeliangroups (Y)$.
    Then $f_{\ast}J^{\ast}$ is a flasque resolution of $f_{\ast}\mathcal{F}$.
\end{reason}
\begin{remark}[\textbf{\emph{Gabber Theorem}}]
    Let $X$ be a scheme.
    Then $\quasicoherent (X)$ has enough injective objects.
\end{remark}
\begin{remark}
    Let $X$ be a scheme.
    Suppose that X is either noetherian or quasi-compact and separated.
    Then the right derived functor of $\Gamma(X, \cdot): \quasicoherent (X) \longrightarrow \abeliangroups$ coincide with $H^{i}(X), \cdot$.
    In fact, this property is equivalent to each injective object is $\Gamma(X, \cdot)$-acyclic.
\end{remark}
\begin{theorem}[\textbf{\emph{Grothendieck Vanishing}}]
    Let $X$ be a noetherian topological space of dimension $n < \infty$.
    Then for all $\mathcal{F}\in \abeliangroups (X)$, we have that $H^{i}(X, \mathcal{F}) = 0$ for all $i > n$.
    \label{Theorem 2.1}
\end{theorem}

\subsection{Cohomology of noetherian affine schemes}
\label{subsection:Sheaf_Cohomology_Cohomology_of_noetherian_affine_schemes}

\begin{theorem}[\textbf{\emph{Artin-Rees}}]
    Let $A$ be a noetherian ring, $M \subseteq N$ finitely generated $A$-modules, $\mathfrak{a} \subseteq A$ ideal.
    Then for all $n > 0$, there exists $m > n$ such that $\mathfrak{a}M \supseteq M \cap a^{m}N$.
    \vspace{-\baselineskip} % 减少一行间距
    \label{Theorem 2.2}
\end{theorem}
\begin{remark}
    This theorem says that the $\mathfrak{a}$-adic topology of M is compatible with the induced topology of $\mathfrak{a}$-adic topology of $N$ on $M$. 
\end{remark}
\begin{lemma}
    Let $A$ be a noetherian ring, $I$ an injective $A$-module, $\mathfrak{a} \subseteq A$ ideal.
    Assume $J \subseteq I$ is the $A$-submodule consist of $x\in I$ such that $\mathfrak{a}^{n}x= 0$ for some $n > 0$.
    Then $J$ is injective.
    \label{Lemma 2.1}
\end{lemma}
\begin{proof}
    It suffices to show that for all $\mathfrak{b} \subseteq A$ ideal and $\varphi: \mathfrak{b} \longrightarrow J$ homomorphism of $A$-modules,
    there exists $\psi: A \longrightarrow J$ extending $\varphi$ satisfies the following diagram commutes
    \begin{equation}
        \begin{tikzcd}
            \mathbf{b} \arrow[r, hookrightarrow] \arrow[d, "\varphi"] &
            A \arrow[dl, "\psi"] \\
            J &
        \end{tikzcd}
    \end{equation}
    \par
    Since $A$ is noetherian, $B$ is finitely generated.
    Thus there exists $n > 0$ such that $\mathfrak{a}^{n}\varphi(\mathfrak{b}) = 0$.
    By Artin-Rees, there exists $m > n$ such that $\mathfrak{a}^{n}\mathfrak{b} \supseteq \mathfrak{b} \cap \mathfrak{a}^{m}$.
    Thus $\varphi(\mathfrak{b} \cap \mathfrak{a}^{m}) = 0$ so that $\varphi$ factors through $\mathfrak{b}/(\mathfrak{b} \cap \mathfrak{a}^{m})$.
    Consider $\varphi_{I}: \mathfrak{b}/(\mathfrak{b} \cap \mathfrak{a}^{m}) \longrightarrow J \hookrightarrow I$.
    As $I$ is injective, $\varphi_{I}$ extends to $\psi_{I}: A/\mathfrak{a}^{m} \longrightarrow I$.
    Note that $im(\psi_{I}) \subseteq J$ since $\mathfrak{a}^{m}im(\psi{I}) = 0$, get $\psi$. 
\end{proof}
\begin{lemma}
    Let $A$ be a noetherian ring, $I$ an injective $A$-module.
    Then for all $f\in A$, the localization $\theta: I \longrightarrow I_{f}$ is surjective.
    \label{Lemma 2.2}
\end{lemma}
\begin{proof}
    For all $i > 0$, set $\mathfrak{b}_{i} = \annihilator_{A}(f^{i})$.
    Get an increasing sequence of ideals $\mathfrak{b}_{1} \subseteq \mathfrak{b}_{2} \subseteq \cdots$.
    As $A$ is noetherian, $\{\mathfrak{b}_{i}\}$ stabilize from $\mathfrak{b}_{r}$ for some $r < \infty$.
    For $x\in I_{f}$, we can write $x = \frac{\theta(y)}{f^{n}}$ where $y\in I$ and $n > 0$.
    There is a canonical homomorphism $\varphi: (f^{n + r}) \longrightarrow I\quad f^{n + r} \longmapsto f^{r}y$.
    Easy to check that $\varphi$ is well defined.
    Since $I$ is injective, $\varphi$ extends to $\psi: A \longrightarrow I$.
    Set $z = \psi(1)$, then $f^{n + r}z = f^{r}y$.
    Thus $\theta(z) = \frac{z}{1} = \frac{f^{n + r}z}{f^{n + r}} = \frac{f^{r}y}{f^{n + r}} = \frac{\theta(y)}{f^{n}} = x$ so that $\theta$ is surjective.
\end{proof}
\begin{proposition}
    Let $A$ be a noetherian ring, $I$ an injective $A$-module.
    Then $\widetilde{I}$ is flasque on $X = \spec A$.
    \label{Proposition 2.6}
\end{proposition}
\begin{proof}
    Set $Y = Supp(\widetilde{I}) = \{x\in X \big{|} \widetilde{I}_{x} \neq 0\} \subseteq X$ closed.
    If $Y = \varnothing$, then $\widetilde{I}$ is flasque.
    If $Y \neq \varnothing$, since $A$ is noetherian, we can assume for all injective $A$-module $J$ with support $\support (\widetilde{J}) \subsetneq Y$, $\widetilde{J}$ is flasque.
    Want to show $\widetilde{I}(X) \longrightarrow \widetilde{I}(U)$ is surjective for all open subset $U \subseteq X$.
    \par
    If $Y \cap U = \varnothing$, then $\widetilde{I}(U) = 0$, done!
    If $Y \cap U \neq \varnothing$, take standard open subset $D(f) \subseteq U$ and $D(f) \cap Y \neq \varnothing$.
    Set $Z = X \setminus D(f)$.
    Let $s\in \widetilde{I}(U)$, then $s\big{|}_{D(f)} \subseteq \widetilde{I}(D(f)) = I_{f}$.
    By Lemma \ref{Lemma 2.2}, we can lift $s\big{|}_{D(f)}$ to $t\in \widetilde{I}(X) = I$.
    Thus $(s - t\big{|}_{U})\big{|}_{D(f)} = 0$ so that $(s - t\big{|}_{U})\in \Gamma_{Z \cap U}(U, \widetilde{I}\big{|}_{U})$ i.e. support of it is in $Z$.
    Remains to show $\Gamma_{Z}(X, \widetilde{I}) \longrightarrow \Gamma_{Z \cap U}(U, \widetilde{I}\big{|}_{U})$.
    \par
    Note that $J = \Gamma_{Z}(X, \widetilde{I})$ is exactly the submodule consist of $x\in I$ such that $f^{n}x = 0$ for some $n > 0$.
    By Lemma \ref{Lemma 2.1}, $J$ is injective $A$-module with $Supp(\widetilde{J}) \subsetneq Y$.
    By induction hypothesis, $\widetilde{J}$ is flasque.
    Thus $\widetilde{J}(X) \longrightarrow \widetilde{J}(U)$ is surjective.
    While $\widetilde{J}(X) = \Gamma_{Z}(X, \widetilde{I})$ and $\widetilde{J}(U) = \Gamma_{Z \cap U}(U, \widetilde{I}\big{|}_{U})$, done!
\end{proof}
\begin{theorem}[\textbf{\emph{Serre Vanishing}}]
    Let $A$ be a noetherian ring and $X = \spec A$.
    Then for all $\mathcal{F}$ quasi-coherent sheaf in $X$, we have that $H^{i}(X, \mathcal{F}) = 0$ for all $i > 0$.
    \label{Theorem 2.3}
\end{theorem}
\begin{proof}
    For $\mathcal{F}$ quasi-coherent, set $M = \mathcal{F}(X)$.
    Take injective resolution $I^{\ast}$ of $M$ in $Mod_{A}$.
    Thus $0 \longrightarrow \mathcal{F} \longrightarrow \widetilde{I^{0}} \longrightarrow \cdots$ is exact, which is a $\Gamma(X, \cdot)$-acyclic resolution by Proposition \ref{Proposition 2.6}.
    As $\widetilde{I^{i}}$ is $\Gamma(X, \cdot)$-acyclic, can apply $\Gamma(X, \cdot)$ to calculate $H^{i}(X, \mathcal{F})$.
    But $\Gamma(X, \cdot)$ gives back to $0 \longrightarrow M \longrightarrow I^{0} \longrightarrow \cdots$ exact, get $H^{i}(X, \mathcal{F}) = 0$ for all $i > 0$. 
\end{proof}
\begin{corollary}
    Let $X$ be a noetherian affine scheme.
    Then for all exact sequence $0 \longrightarrow \mathcal{F} \longrightarrow \mathcal{G} \longrightarrow \mathcal{H} \longrightarrow 0$ of $\mathcal{O}_{X}$-module with $\mathcal{F}$ quasi-coherent,
    we have that $0 \longrightarrow \mathcal{F}(X) \longrightarrow \mathcal{G}(X) \longrightarrow \mathcal{H}(X) \longrightarrow 0$ is exact.
    \label{Corollary 2.4}
\end{corollary}
\begin{corollary}
    Let $X$ be a noetherian scheme.
    Suppose that $0 \longrightarrow \mathcal{F} \longrightarrow \mathcal{G} \longrightarrow \mathcal{H} \longrightarrow 0$ is an exact sequence of $\mathcal{O}_{X}$-module.
    If $\mathcal{F}$ and $\mathcal{H}$ are both quasi-coherent (resp. coherent), then $\mathcal{G}$ is quasi-coherent (resp. coherent).
    \label{Corollary 2.5} 
\end{corollary}
\begin{proof}
    Can assume that $X = \spec A$ is affine.
    We have a commutative diagram with exact rows
    \begin{equation}
        \begin{tikzcd}
            0 \arrow[r] &
            \widetilde{\mathcal{F}(X)} \arrow[r] \arrow[d, "\sim"] &
            \widetilde{\mathcal{G}(X)} \arrow[r] \arrow[d] &
            \widetilde{\mathcal{H}(X)} \arrow[r] \arrow[d, "\sim"] & 
            0 \\
            0 \arrow[r] &
            \mathcal{F} \arrow[r] &
            \mathcal{G} \arrow[r] &
            \mathcal{H} \arrow[r] & 
            0
        \end{tikzcd}
    \end{equation}
    Thus by 5 Lemma, $\mathcal{G}$ is quasi-coherent.
    \par
    If moreover $\mathcal{F}$ and $\mathcal{H}$ are coherent, then $\mathcal{F}(X)$ and $\mathcal{H}(X)$ are finitely generated.
    Then $\mathcal{G}(X)$ is also finitely generated so that $\mathcal{G}$ is coherent.
\end{proof}
\begin{lemma}
    Let $X$ be a noetherian scheme.
    Assume that $H^{1}(X, \mathcal{I}) = 0$ for all $\mathcal{I}$ coherent ideal sheaf.
    Then we can cover $X$ by affine open subsets of the form $X_{f}$ for $f\in A = \Gamma(X, \mathcal{O}_{X})$.
    \vspace{-\baselineskip} % 减少一行间距
    \label{Lemma 2.3}
\end{lemma}
\begin{proof}
    Suffice to show that every closed point $x\in X$ admits an affine open neighbourhood $X_{f}$.
    For $x\in X$ closed point, choose affine open neighbourhood $U$ of $x$ and set $Y = X \setminus U$.
    Get $0 \longrightarrow \mathcal{I}_{Y \cup \{x\}} \longrightarrow \mathcal{I}_{Y} \longrightarrow i_{\ast}\mathcal{O}_{\{x\}} \longrightarrow 0$  is exact with reduced scheme structures on each set,
    where $i: \{x\} \longrightarrow X$ is inclusion.
    By assumption, $\Gamma(X, \mathcal{I}_{Y}) \longrightarrow \Gamma(X, i_{\ast}\mathcal{O}_{\{x\}})$ is surjective.
    Take $f\in \Gamma(X, \mathcal{I}_{Y})$ such that $f$ is mapped to $1$.
    Then $x\in X_{f}$.
    On the other hand, $X_{f} \subseteq U$, get $X_{f}$ is affine.
\end{proof}
\begin{lemma}
    Let $X$ be a noetherian scheme.
    Assume that $H^{1}(X, \mathcal{I}) = 0$ for all $\mathcal{I}$ coherent ideal sheaf.
    Then for all $e > 0$ and $\mathcal{F} \subseteq \mathcal{O}_{X}^{\oplus r}$ coherent, we have that $H^{1}(X, \mathcal{F}) = 0$.
    \label{Lemma 2.4}
\end{lemma}
\begin{proof}
    Define filtration $\mathcal{F} \supseteq \mathcal{F} \cap \mathcal{O}_{X}^{\oplus (r - 1)} \supseteq \cdots \supseteq \mathcal{F} \cap \mathcal{O}_{X} \supseteq 0$ such that the associated quotients are coherent ideal sheaves.
    By long exact sequence and induction, get $H^{1}(X, \mathcal{F} \cap \mathcal{O}_{X}^{i}) = 0$ for all $i > 0$ so that $H^{1}(X, \mathcal{F}) = 0$.
\end{proof}
\begin{theorem}[\textbf{\emph{Serre, Cohomology Criterion of Affineness}}]
    Let $X$ be a noetherian scheme.
    Then the following conditions are equivalent: \\
    (1)$X$ is affine \\
    (2)$H^{i}(X, \mathcal{F}) = 0$ for all $i > 0$ and $\mathcal{F}$ quasi-coherent. \\
    (3)$H^{1}(X, \mathcal{I}) = 0$ for all $\mathcal{I}$ coherent ideal sheaf.
    \label{Theorem 2.4}
\end{theorem}
\begin{proof}
    See in the Hartshorne Chapter III p.215-216.
\end{proof}
\begin{remark}
    In fact, noetherian condition is not necessary.
\end{remark}

\subsection{Čech cohomology}
\label{subsection:Sheaf_Cohomology_Čech_cohomology}

\begin{definition}
    Let $X$ be a topological space, $\mathcal{U} = \{U_{i}\}_{i\in I}$ open covering of $X$ with well-ordered index set I, $\mathcal{F}$ sheaf of abelian groups on $X$.
    For $i_{0}, \cdots, i_{p}\in I$, set $U_{i_{0}, \cdots, i_{p}} = U_{i_{0}} \cap \cdots \cap U_{i_{p}}$.
    Define complex $C^{\ast}(\mathcal{I}, \mathcal{F})$ to be 
    \begin{equation}
        C^{p}(\mathcal{U}, \mathcal{F}) = \prod_{i_{0}, \cdots, i_{p}} \mathcal{F}(U_{i_{0}, \cdots, i_{p}})
    \end{equation}
    with coboundary map 
    \begin{equation}
        \begin{split}
            d^{p}: C^{p}(\mathcal{U}, \mathcal{F}) & \longrightarrow C^{p + 1}(\mathcal{U}, \mathcal{F}) \\
            \alpha = (\alpha_{i_{0}, \cdots, i_{p}})_{i_{0}, \cdots, i_{p}} & \longmapsto (\sum_{k = 0}^{p + 1} (-1)^{k}\alpha_{i_{0}, \cdots, \widehat{i_{k}}, \cdots, i_{p + 1}}\big{|}_{U_{i_{0}, \cdots, i_{p + 1}}})_{i_{0}, \cdots, i_{p + 1}}
        \end{split}
    \end{equation}
\end{definition}
\begin{remark}
    If we don't assume that $I$ is well-ordered, we need to set $U_{i_{0}, \cdots, i_{p}} = 0$ if there are repeated index and $\alpha_{i_{0}, \cdots, i_{p}} = (-1)^{sgn(\sigma)}\alpha_{i_{\sigma(0)}, \cdots, i_{\sigma(p)}}$.
\end{remark}
\begin{definition}
    Let $X$ be a topological space, $\mathcal{U} = \{U_{i}\}_{i\in I}$ open covering of $X$ with well-ordered index set $I$, $\mathcal{F}$ sheaf of abelian groups on $X$.
    Define $\check{H}^{p}(\mathcal{U}, \mathcal{F}) = h^{p}(C^{\ast}(\mathcal{U}, \mathcal{F}))$, called the pth Čech cohomology of $\mathcal{F}$ with respect to $\mathcal{U}$.
\end{definition}
\begin{example}
    (1)For any $\mathcal{F}$ and $\mathcal{U}$, $\check{H}^{0}(\mathcal{U}, \mathcal{F}) = \Gamma(X, \mathcal{F})$. \\
    (2)For $\mathcal{U} = \{X\}$, $\check{H}^{p}(\mathcal{U}, \mathcal{F}) = 0$ for all $p > 0$.
\end{example}
\begin{lemma}
    Let $X$ be a topological space, $\mathcal{U} = \{U_{i}\}_{i\in I}$ open covering of $X$ with well-ordered index set $I$, $\mathcal{F}$ sheaf of abelian groups on $X$.
    Suppose that $\mathcal{U}$ contains $U_{i} = X$ for some $i$.
    Then $0 \longrightarrow \mathcal{F}(X) \longrightarrow C^{\ast}(\mathcal{U}, \mathcal{F})$ is exact.
    \label{Lemma 2.5}
\end{lemma}
\begin{proof}
    Obviously, exactness at $\mathcal{F}(X)$ and $C^{0}(\mathcal{U}, \mathcal{F})$ is ok.
    For $p \ge 1$, without loss of generality, may assume that $i = 0$ which is the smallest element.
    Define homotopy $k^{p}: C^{p}(\mathcal{U}, \mathcal{F}) \longrightarrow C^{p - 1}(\mathcal{U}, \mathcal{F})\quad \alpha \longmapsto (\alpha_{0, i_{0}, \cdots, i_{p - 1}})_{i_{0}, \cdots, i_{p - 1}}$.
    Check that $d^{p - 1} \circ k^{p} + k^{p + 1} \circ d^{p} = \identity_{C^{\ast}(\mathcal{U}, \mathcal{F})}$.
    Thus identity is homotopic to zero map, which inducing $\check{H}^{p}(\mathcal{U}, \mathcal{F}) = 0$ for all $p > 0$.. 
\end{proof}

\subsection{Comparison Theorem}
\label{subsection:Sheaf_Cohomology_Comparison_Theorem}

\begin{definition}
    Let $X$ be a topological space, $\mathcal{U} = \{U_{i}\}_{i\in I}$ open covering of $X$ with well-ordered index set $I$, $\mathcal{F}$ sheaf of abelian groups on $X$.
    Define a complex of sheaves on $X$, denoted by $\mathcal{C}^{\ast}(\mathcal{U}, \mathcal{F})$, as following
    \begin{equation}
        \mathcal{C}^{p}(\mathcal{U}, \mathcal{F}) = \prod_{i_{0}, \cdots, i_{p}} f_{\ast}(\mathcal{F}\big{|}_{U_{i_{0}, \cdots, i_{p}}})
    \end{equation}
    where $f$ is the inclusion, with coboundary map
    \begin{equation}
        d^{p}: \mathcal{C}^{p}(\mathcal{U}, \mathcal{F}) \longrightarrow \mathcal{C}^{p + 1}(\mathcal{U}, \mathcal{F})
    \end{equation}
    defined accordingly.
\end{definition}
\begin{remark}
    Obviously, $\Gamma(X, \mathcal{C}^{p}(\mathcal{U}, \mathcal{F})) = C^{p}(\mathcal{U}, \mathcal{F})$.
\end{remark}
\begin{proposition}
    Let $X$ be a topological space, $\mathcal{U} = \{U_{i}\}_{i\in I}$ open covering of $X$ with well-ordered index set $I$, $\mathcal{F}$ sheaf of abelian groups on $X$.
    Then $0 \longrightarrow \mathcal{F} \longrightarrow \mathcal{C}^{\ast}(\mathcal{U}, \mathcal{F})$ is exact.
    \vspace{-\baselineskip} % 减少一行间距
    \label{Proposition 2.7}
\end{proposition}
\begin{reason}
    Since exactness of complex of sheaves is equivalent to exactness at all stalks.
    Set $x\in X$, we can represent elements in stalks by sections on $V$, which is small enough to be contained in $U_{j}$ for some $j$.
    Apply Lemma \ref{Lemma 2.5}, get exactness of complex of sections on $V$.
\end{reason}
\begin{proposition}
    Let $X$ be a topological space, $\mathcal{U} = \{U_{i}\}_{i\in I}$ open covering of $X$ with well-ordered index set $I$, $\mathcal{F}$ flasque sheaf of abelian groups on $X$.
    Then $\check{H}^{p}(\mathcal{U}, \mathcal{F}) = 0$ for all $p > 0$.
    \vspace{-\baselineskip} % 减少一行间距
    \label{Proposition 2.8}
\end{proposition}
\begin{proof}
    Since flasque is stable under restriction to open subset, direct limit and product, $\mathcal{C}^{p}(\mathcal{U}, \mathcal{F})$ is flasque for all $p$.
    Thus $\mathcal{C}^{\ast}(\mathcal{U}, \mathcal{F})$ is a flasque resolution of $\mathcal{F}$.
    By Proposition \ref{Proposition 2.5} and Proposition \ref{Proposition 2.1}, get
    \begin{equation}
        \check{H}^{p}(\mathcal{U}, \mathcal{F}) = h^{p}(\Gamma(X, \mathcal{C}^{\ast}(\mathcal{U}, \mathcal{F}))) = H^{p}(X, \mathcal{F}) = 0
    \end{equation}
    hence we are done!
\end{proof}
\begin{lemma}
    Let $X$ be a topological space, $\mathcal{U} = \{U_{i}\}_{i\in I}$ open covering of $X$ with well-ordered index set $I$, $\mathcal{F}$ sheaf of abelian groups on $X$.
    Then for all $p \ge 0$, there is a natural homomorphism $\check{H}^{p}(\mathcal{U}, \mathcal{F}) \longrightarrow H^{p}(X, \mathcal{F})$.
    \label{Lemma 2.6}
\end{lemma}
\begin{proof}
    Let $0 \longrightarrow \mathcal{F} \longrightarrow \mathcal{I}^{\ast}$ be an injective resolution of $\mathcal{F}$ in $Ab(X)$. 
    By Comparison Theorem in Homological Algebra, there exists a morphism of complexes which is unique up to homotopy,
    inducing the natural homomorphisms we want.
\end{proof}
\begin{theorem}[\textbf{\emph{Comparison Theorem}}]
    Let $X$ be a topological space, $\mathcal{U} = \{U_{i}\}_{i\in I}$ open covering of $X$ with well-ordered index set $I$, $\mathcal{F}$ sheaf of abelian groups on $X$.
    Suppose that for all $p$ and all $i_{0}, \cdots, i_{p}$, we have that $H^{q}(U_{i_{0}, \cdots, i_{p}}, \mathcal{F}\big{|}_{U_{i_{0}, \cdots, i_{p}}}) = 0$ for all $q > 0$.
    Then the natural homomorphism $\check{H}^{r}(\mathcal{U}, \mathcal{F}) \longrightarrow H^{r}(X, \mathcal{F})$ is isomorphic for all $r \ge 0$.
    \label{Theorem 2.5}
\end{theorem}
\begin{proof}
    For $r = 0$, the natural homomorphism is identity map of global sections of $\mathcal{F}$.
    For $r > 0$, embed $\mathcal{F}$ into an injective sheaf $\mathcal{I}$.
    There is an exact sequence
    \begin{equation}
        0 \longrightarrow \mathcal{F} \longrightarrow \mathcal{I} \longrightarrow \mathcal{G} \longrightarrow 0
    \end{equation}
    On the one hand, by definition of Čech sheaf resolution, we have an exact sequence of complexes
    \begin{equation}
        \begin{tikzcd}
            0 \arrow[r] &
            \mathcal{F} \arrow[r] \arrow[d] &
            \mathcal{I} \arrow[r] \arrow[d] &
            \mathcal{G} \arrow[r] \arrow[d] &
            0 \\
            0 \arrow[r] &
            \mathcal{C}^{\bullet}(\mathcal{U}, \mathcal{F}) \arrow[r] &
            \mathcal{C}^{\bullet}(\mathcal{U}, \mathcal{I}) \arrow[r] &
            \mathcal{C}^{\bullet}(\mathcal{U}, \mathcal{G}) \arrow[r] &
            0
        \end{tikzcd}
    \end{equation}
    Taking products, get
    \begin{equation}
        0 \longrightarrow C^{\ast}(\mathcal{U}, \mathcal{F}) \longrightarrow C^{\ast}(\mathcal{U}, \mathcal{I}) \longrightarrow C^{\ast}(\mathcal{U}, \mathcal{G}) \longrightarrow 0
    \end{equation}
    On the other hand, by Horseshoe Lemma, we may take injective resolution $\mathcal{I}_{\mathcal{F}}^{\bullet}$, $\mathcal{I}_{\mathcal{I}}^{\bullet}$ and $\mathcal{I}_{\mathcal{G}}^{\bullet}$ of $\mathcal{F}$, $\mathcal{I}$ and $\mathcal{G}$ respectively such that
    \begin{equation}
        \begin{tikzcd}
            0 \arrow[r] &
            \mathcal{F} \arrow[r] \arrow[d] &
            \mathcal{I} \arrow[r] \arrow[d] &
            \mathcal{G} \arrow[r] \arrow[d] &
            0 \\
            0 \arrow[r] &
            \mathcal{I}_{\mathcal{F}}^{\bullet} \arrow[r] &
            \mathcal{I}_{\mathcal{I}}^{\bullet} \arrow[r] &
            \mathcal{I}_{\mathcal{G}}^{\bullet} \arrow[r] &
            0
        \end{tikzcd}
    \end{equation}
    is an exact sequence of complexes and $\mathcal{I}_{\mathcal{I}}^{i} = \mathcal{I}_{\mathcal{F}}^{i} \oplus \mathcal{I}_{\mathcal{G}}^{i}$ for all $i \ge 0$.
    Then by Comparison Theorem for injective resolution, 
    we get morphism of chain complexes $\alpha: \mathcal{C}^{\bullet}(\mathcal{U}, \mathcal{F}) \rightarrow \mathcal{I}_{\mathcal{F}}^{\bullet}$, $\beta: \mathcal{C}^{\bullet}(\mathcal{U}, \mathcal{I}) \rightarrow \mathcal{I}_{\mathcal{I}}^{\bullet}$ and $\gamma: \mathcal{C}^{\bullet}(\mathcal{U}, \mathcal{G}) \rightarrow \mathcal{I}_{\mathcal{G}}^{\bullet}$,
    which are unique up to homotopy.
    \par
    Consider the following diagram
    \begin{equation}
        \begin{tikzcd}
            0 \arrow[r] &
            \mathcal{C}^{i}(\mathcal{U}, \mathcal{F}) \arrow[r, hookrightarrow, "f"] \arrow[d, "\alpha"] &
            \mathcal{C}^{i}(\mathcal{U}, \mathcal{I}) \arrow[r, "g"] \arrow[d, "\beta"] &
            \mathcal{C}^{i}(\mathcal{U}, \mathcal{G}) \arrow[r] \arrow[d, "\gamma"] &
            0 \\
            0 \arrow[r] &
            \mathcal{I}_{\mathcal{F}}^{i} \arrow[r, hookrightarrow, "u"] &
            \mathcal{I}_{\mathcal{I}}^{i} \arrow[r, "v"] &
            \mathcal{I}_{\mathcal{G}}^{i} \arrow[r] &
            0
        \end{tikzcd}
    \end{equation}
    Want to modify $\alpha$, $\beta$ and $\gamma$.
    Since the bottom row is split, we have inclusion $\sigma: \mathcal{I}_{\mathcal{G}}^{\bullet} \rightarrow \mathcal{I}_{\mathcal{I}}^{\bullet}$ and projection $\pi: \mathcal{I}_{\mathcal{I}}^{\bullet} \rightarrow \mathcal{I}_{\mathcal{F}}^{\bullet}$.
    Take $\beta' = \beta + \pi \circ (\gamma \circ g - v \circ \beta)$ and $\alpha' = \sigma \circ (\beta' \circ f - u \circ \alpha)$.
    Then by our choice of $\alpha$, $\beta$ and $\gamma$, it is clear that the new diagram is commutative.
    \par
    By assumption, for all $i_{0}, \cdots, i_{p}$,
    \begin{equation}
        0 \longrightarrow \mathcal{F}(U_{i_{0}, \cdots, i_{p}})\longrightarrow \mathcal{I}(U_{i_{0}, \cdots, i_{p}}) \longrightarrow \mathcal{G}(U_{i_{0}, \cdots, i_{p}}) \longrightarrow 0
    \end{equation}
    is exact.
    Taking global sections and by Homological Algebra, there is commutative daigram between two long exact sequences
    \begin{equation}
        \begin{tikzcd}
            \cdots \arrow[r] &
            \check{H}^{r}(\mathcal{U}, \mathcal{F}) \arrow[r] \arrow[d] &
            \check{H}^{r}(\mathcal{U}, \mathcal{I}) \arrow[r] \arrow[d] &
            \check{H}^{r}(\mathcal{U}, \mathcal{G}) \arrow[r] \arrow[d] &
            \check{H}^{r + 1}(\mathcal{U}, \mathcal{F}) \arrow[r] \arrow[d] &
            \cdots \\
            \cdots \arrow[r] &
            H^{r}(X, \mathcal{F}) \arrow[r] &
            H^{r}(X, \mathcal{I}) \arrow[r] &
            H^{r}(X, \mathcal{G}) \arrow[r] &
            H^{r + 1}(X, \mathcal{F}) \arrow[r] &
            \cdots
        \end{tikzcd}
    \end{equation}
    Since $\mathcal{I}$ is injective, get $\mathcal{I}$ flasque and $\check{H}^{r}(\mathcal{U}, \mathcal{I}) = 0$ for all $r > 0$.
    Thus $\check{H}^{r + 1}(\mathcal{U}, \mathcal{F}) = \check{H}^{r}(\mathcal{U}, \mathcal{G})$ and $H^{r + 1}(X, \mathcal{F}) = H^{r}(X, \mathcal{G})$ for all $r \ge 1$.
    In particular, we have commutative diagram with exact rows
    \begin{equation}
        \begin{tikzcd}
            0 \arrow[r] &
            \check{H}^{0}(\mathcal{U}, \mathcal{F}) \arrow[r] \arrow[d, equal] &
            \check{H}^{0}(\mathcal{U}, \mathcal{I}) \arrow[r] \arrow[d, equal] &
            \check{H}^{0}(\mathcal{U}, \mathcal{G}) \arrow[r] \arrow[d, equal] &
            \check{H}^{1}(\mathcal{U}, \mathcal{F}) \arrow[r] \arrow[d] &
            0 \\
            \cdots \arrow[r] &
            H^{0}(X, \mathcal{F}) \arrow[r] &
            H^{0}(X, \mathcal{I}) \arrow[r] &
            H^{0}(X, \mathcal{G}) \arrow[r] &
            H^{1}(X, \mathcal{F}) \arrow[r] &
            0
        \end{tikzcd}
    \end{equation}
    Hence by 5 Lemma, we get the natural map $\check{H}^{1}(\mathcal{U}, \mathcal{F}) \rightarrow H^{1}(X, \mathcal{F})$ is isomorphic.
    Finally, by induction, done!
\end{proof}
\begin{remark}
    Here our modifying assumption is in fact same as the proof of injectivity of a split exact sequence consists of injective objects.
\end{remark}
\begin{corollary}
    Let $X$ be a (noetherian) separated scheme, $\mathcal{U}$ affine open covering of $X$, $\mathcal{F}$ quasi-coherent sheaf on $X$.
    Then the natural homomorphism $\check{H}^{p}(\mathcal{U}, \mathcal{F}) \longrightarrow H^{p}(X, \mathcal{F})$ is isomorphic for all $p$.
    \label{Corollary 2.6}
\end{corollary}
\begin{remark}
    This corollary immediately comes from Serre Vanishing Theorem.
\end{remark}
\begin{corollary}
    Let $X$ be a (noetherian) separated scheme covered by $r + 1$ affine open subsets.
    Then for all $\mathcal{F}$ quasi-coherent on $X$, we have that $H^{i}(X, \mathcal{F}) = 0$ for all $i > r$.
    In particular, when $r = 0$, this specializes to Serre Vanishing Theorem.
    \label{Corollary 2.7}
\end{corollary}

\subsection{Cohomology of projective space}
\label{subsection:Sheaf_Cohomology_Cohomology_of_projective_space}

\begin{theorem}
    Let $A$ be a noetherian ring, $S= A[x_{0}, \cdots, x_{r}]$, $X = \proj(S) = \mathbb{P}_{A}^{r}$, $r \ge 1$.
    Then we have that \\ 
    (1)$H^{i}(X, \mathcal{O}_{X}(n)) = 0$ for all $0 < i < r$ and all $n\in \mathbb{Z}$ \\
    (2)$H^{r}(X, \mathcal{O}_{X}(-r - 1)) \cong A$ is free $A$-module of rank $1$ \\
    (3)the natural pairing $H^{0}(X, \mathcal{O}_{X}(n)) \times H^{r}(X, \mathcal{O}_{X}(-n - r - 1)) \longrightarrow H^{r}(X, \mathcal{O}_{X}(-r - 1))$ is a perfect pairing of finite free $A$-modules for all $n\in \mathbb{Z}$.
    \label{Theorem 2.6}
\end{theorem}
\begin{remark}
    In fact, we have already known that $H^{0}(X, \mathcal{O}_{X}(n)) =
    \left\{
        \begin{aligned}
            & S_{n} & n \ge 0 \\
            & 0 & n < 0
        \end{aligned}
    \right.$
    and $H^{i}(X, \mathcal{O}_{X}(n)) = 0$ for all $i > r$ and all $n\in \mathbb{Z}$.
    Thus with this theorem, we have figured out all the cohomological groups of $\mathbb{P}_{A}^{r}$.
    Especially, all of them are finite free $A$-modules.
\end{remark}
\begin{proof}
    Consider $\mathcal{F} = \oplus_{n\in \mathbb{Z}} \mathcal{O}_{X}(n)$ quasi-coherent.
    Since cohomology commutes with direct sum, $H^{i}(X, \mathcal{F}) = \oplus_{n\in \mathbb{Z}} H^{i}(X, \mathcal{F})$.
    In particular, $H^{0}(X, \mathcal{F}) = \Gamma_{\ast}(\mathcal{O_{X}}) \cong S$.
    Note that $X$ is noetherian, separated and covered by $r + 1$ affine open subsets.
    By Corollary \ref{Corollary 2.7}, get $\check{H}^{p}(\mathcal{U}, \mathcal{F}) \cong H^{p}(X, \mathcal{F})$ for all $p$.
    \par
    For all $i_{0}, \cdots, i_{p}$, note that $U_{i_{0}, \cdots, i_{p}} = D_{+}(x_{i_{0}}, \cdots, x_{i_{p}})$.
    Get $\mathcal{F}(U_{i_{0}, \cdots, i_{p}}) \cong S_{x_{i_{0}}, \cdots, x_{i_{p}}}$. 
    Thus $C^{\ast}(\mathcal{U}, \mathcal{F})$ is given by 
    \begin{equation}
        0 \longrightarrow \prod_{i_{0}} S_{x_{i_{0}}} \longrightarrow \cdots \longrightarrow S_{x_{0}, \cdots, x_{r}}.
    \end{equation}
    Since $\check{H}^{r}(\mathcal{U}, \mathcal{F})$ is the cokernel of $d^{r - 1}: \prod_{k} S_{x_{0}, \cdots, \widehat{x_{k}}, \cdots, x_{r}} \longrightarrow S_{x_{0}, \cdots, x_{r}}$.
    Note that $S_{x_{0}, \cdots, x_{r}}$ is free $A$-module spanned by $\{x_{0}^{l_{0}}..x_{r}^{l_{r}}\}$, where $l_{0}, \cdots, l_{r}\in \mathbb{Z}$.
    In addition, $im(d^{r - 1})$ is free $A$-module spanned by $\{x_{0}^{l_{0}}\cdots x_{r}^{l_{r}}\}$, where $l_{0}, \cdots, l_{r}\in \mathbb{Z}$ and at least one $l_{i} \ge 0$.
    Get $H^{r}(\mathcal{U}, \mathcal{F})$ is free $A$-module spanned by $\{x_{0}^{l_{0}}\cdots x_{r}^{l_{r}}\}$, where $l_{i} < 0$.
    While the only "monomial" of degree $-r - 1$ is $x_{0}^{-1}\cdots x_{r}^{-1}$, get $H^{r}(X, \mathcal{O}_{X}(-r - 1)) \cong A$.
    \par
    For (3), we also find $H^{r}(X, \mathcal{O}_{X}(-n - r - 1)) = 0$ if $n < 0$.
    On the other hand, $H^{0}(X, \mathcal{O}_{X}(n)) = 0$ if $n < 0$.
    Thus, (3) is trivially true for $n < 0$.
    For $n \ge 0$, $H^{0}(X, \mathcal{O}_{X}(n))$ has basis $\{x_{0}^{{m_{0}}}\cdots x_{r}^{m_{r}}\}$,
    where $m_{i} \ge 0$ and $\sum_{i = 0}^{r} m_{i} = n$.
    The natural pairing is generated by $(x_{0}^{m_{0}}\cdots x_{r}^{m_{r}}, x_{0}^{l_{0}}\cdots x_{r}^{l_{r}}) \longmapsto x_{0}^{m_{0} + l_{0}}\cdots x_{r}^{m_{r} + l_{r}}$,
    here that $x_{i}^{m_{i} + l_{i}} = 0$ if $m_{i} + l_{i} \ge 0$.
    Then it is a perfect pairing since it is easy to see that dual basis of $x_{0}^{m_{0}}\cdots x_{r}^{m_{r}}$ is $x_{0}^{-m_{0} - 1}\cdots x_{r}^{-m_{r} - 1}$.
    \par
    For (1), take induction on $r$.
    When $r = 1$, there is nothing to prove.
    Suppose that $r \ge 2$.
    Consider localization of $C^{\ast}(\mathcal{U}, \mathcal{F})$ with respect to $x_{r}$.
    By Theorem \ref{Theorem 2.1}, the localization gives the Čech complex of $\mathcal{F}\big{|}_{U_{r}}$ with respect to $\mathcal{U}\big{|}_{U_{r}}$.
    As localization is exact and $U_{r}$ is affine, $H^{i}(X, \mathcal{F})_{x_{r}} = H^{i}(U_{r}, \mathcal{F}\big{|}_{U_{r}}) = 0$.
    Suffice to show that for all $0 < i < r$, $x_{r}$ acts injectively on $H^{i}(X, \mathcal{F})$.
    View $x_{r}$ as a homomorphism of $A$-modules like below
    \begin{equation}
        x_{r}: H^{i}(X, \mathcal{F}(-1)) \longrightarrow H^{i}(X, \mathcal{F})
    \end{equation}
    here $\mathcal{F}(-1)$ is same sheaf on $\mathcal{F}$ with grading shifted.
    Consider exact sequence of graded $C$-modules 
    \begin{equation}
        0 \longrightarrow S(-1) \overset{x_{r}}{\longrightarrow} S \longrightarrow S/(x_{r}) \longrightarrow 0
    \end{equation}
    Get exact sequence of sheaves 
    \begin{equation}
        0 \longrightarrow \mathcal{O}_{X}(-1) \overset{x_{r}}{\longrightarrow} \mathcal{O}_{X} \longrightarrow j_{\ast}\mathcal{O}_{H} \longrightarrow 0
    \end{equation}
    where $H$ is the hyperplane given by $x_{r} = 0$ and $j: H \hookrightarrow X$ is closed immersion. 
    Take direct sum, get exact sequence
    \begin{equation}
        0 \longrightarrow \mathcal{F}(-1) \overset{x_{r}}{\longrightarrow} \mathcal{F} \longrightarrow \mathcal{F}_{H} \longrightarrow 0
    \end{equation}
    where $\mathcal{F}_{H} = \oplus_{n\in \mathbb{Z}} j_{\ast}(\mathcal{O}_{H}(n))$. 
    Get long exact sequence
    \begin{equation}
        \cdots \longrightarrow H^{i - 1}(X, \mathcal{F}_{H}) \longrightarrow H^{i}(X, \mathcal{F}(-1)) \overset{x_{r}}{\longrightarrow} H^{i}(X, \mathcal{F}) \longrightarrow H^{i}(X, \mathcal{F})_{H} \longrightarrow \cdots
    \end{equation}
    Now $H \cong \mathbf{P}^{r - 1}_{A}$ and since $j$ is closed immersion, $H^{i}(X, \mathcal{F}_{H}) = H^{i}(H, \oplus_{n\in \mathbb{Z}} O_{H}(n))$.
    By induction hypothesis, $H^{i}(X, \mathcal{F}_{H}) = 0$ for all $0 < i < r - 1$.
    Thus $x_{r}$ is injective on $H^{i}(X, \mathcal{F}(-1))$ for all $1 < i < r$.
    When $i = 1$, find that $H^{0}(X, \mathcal{F}) = S \longrightarrow H^{0}(X, \mathcal{F}_{H}) = S/(x_{r})$ is surjective.
    Get $x_{r}$ is injective on $H^{i}(X, \mathcal{F}(-1))$ for all $0 < i < r$, done!
\end{proof}
\begin{theorem}[\textbf{\emph{Serre}}]
    Let $A$ be a noetherian ring, $X$ projective scheme over $A$, $\mathcal{F}$ coherent sheaf on $X$.
    Then \\
    (1)for all $i \ge 0$, $H^{i}(X, \mathcal{F})$ is a finite $A$-module. \\
    (2)for $j: X \hookrightarrow \mathbb{P}_{A}^{r}$ closed immersion, there exists integer $n_{0}$ relative to $\mathcal{F}$ such that $H^{i}(X, \mathcal{F}(n)) = 0$ for all $i > 0$ and $n \ge n_{0}$.
    \label{Theorem 2.7}
\end{theorem}
\begin{proof}
    Since $j$ is finite, $j_{\ast}(\mathcal{F})$ is coherent on $\mathbb{P}_{A}^{r}$ and by Projection Formula, $j_{\ast}(\mathcal{F}(n)) = (j_{\ast}(\mathcal{F}))(n)$.
    What's more, since $j$ is closed immersion, $H^{i}(X, \mathcal{F}) = H^{i}(\mathbb{P}_{A}^{r}, j_{\ast}(\mathcal{F}))$.
    Thus we can reduce this problem to $X = \mathbb{P}_{A}^{r}$.
    For $\mathcal{F} = \mathcal{O}_{X}(m)$, this is just things told by \ref{Theorem 2.6}.
    Also, for general $\mathcal{F}$, as $\mathbb{P}_{A}^{r}$ can be covered by $r + 1$ affine open subsets, 
    $H^{i}(X, \mathcal{F}(n)) = 0$ for all $i > r$ and $n\in \mathbb{Z}$.
    \par
    For (1), by induction, suppose theorem is correct for $i + 1$.
    By Corollary \ref{Corollary 1.1}, there exists $m\in \mathbb{Z}$ and $r < \infty$ such that $\mathcal{F}$ is quotient of $\mathcal{O}_{X}(m)^{r}$,
    inducing the following exact sequence of coherent sheaves
    \begin{equation}
        0 \longrightarrow \mathcal{G} \longrightarrow \mathcal{O}_{X}(m)^{r} \longrightarrow \mathcal{F} \longrightarrow 0
    \end{equation} 
    Consider the long exact sequence
    \begin{equation}
        \cdots \longrightarrow H^{i}(X, \mathcal{O}_{X}(m)^{r}) \longrightarrow H^{i}(X, \mathcal{F}) \longrightarrow H^{i + 1}(X, \mathcal{G}) \longrightarrow \cdots
    \end{equation}
    By hypothesis, $H^{i + 1}(X, \mathcal{G})$ is finite $A$-module.
    As $A$ is noetherian, $H^{i}(X, \mathcal{F})$ is also finite.
    \par
    For (2), by above discuss, we only need to check for $0 < i \le r$.
    Induct on $i$, assume for $i + 1$ and all coherent sheaf $\mathcal{F}$,
    there exists $n_{i + 1}(\mathcal{F})$ such that $H^{i + 1}(X, \mathcal{F}(n)) = 0$ for all $n \ge n_{i + 1}(\mathcal{F})$.
    Take same short exact sequence.
    Tensor the short exact sequence by $\mathcal{O}_{X}(n)$.
    Get exact sequence
    \begin{equation}
        0 \longrightarrow \mathcal{G}(n) \longrightarrow \mathcal{O}_{X}(m + n)^{r} \longrightarrow \mathcal{F}(n) \longrightarrow 0
    \end{equation}
    Consider the long exact sequence
    \begin{equation}
        \cdots \longrightarrow H^{i}(X, \mathcal{O}_{X}(m + n)^{r}) \longrightarrow H^{i}(X, \mathcal{F}(n)) \longrightarrow H^{i + 1}(X, \mathcal{G}(n)) \longrightarrow \cdots
    \end{equation}
    By hypothesis, there exists $n_{i + 1}(\mathcal{G})$ such that $H^{i + 1}(X, \mathcal{G}(n)) = 0$ for all $n \ge n_{i + 1}(\mathcal{G})$.
    By Theorem \ref{Theorem 2.6}, $H^{i}(X, \mathcal{O}_{X}(m + n)^{r}) = 0$ for large enough $n$.
    Thus there exists $n_{i}(\mathcal{F})$ such that $H^{i}(X, \mathcal{F}(n)) = 0$ for all $n \ge n_{i}(\mathcal{F})$.
    As there are finitely many $i$, we can take a uniform upper $n_{0}(\mathcal{F})$ bound for $n_{i}(\mathcal{F})$.
\end{proof}
\begin{corollary}
    Let $f: X \longrightarrow Y$ be a projective morphism with $X, Y$ noetherian, $\mathcal{F}$ coherent sheaf on $X$.
    Then $f_{\ast}\mathcal{F}$ is coherent on $Y$.
    \label{Corollary 2.8}
\end{corollary}
\begin{reason}
    Can assume $Y = \spec A$.
    Then $f_{\ast}\mathcal{F} \cong \widetilde{H^{0}(X, \mathcal{F})}$ which is a finite $A$-module by Theorem \ref{Theorem 2.7}.
\end{reason}
\begin{corollary}
    Let $X$ be a geometrically integral scheme projective over field $k$.
    Then $\Gamma(X, \mathcal{O}_{X}) = k$.
    \label{Corollary 2.9} 
\end{corollary}
\begin{reason}
    By Theorem \ref{Theorem 2.7}, $L = \Gamma(X, \mathcal{O}_{X})$ is finite over $k$.
    While $X$ is integral, get $L$ is integral domain.
    Thus by Noetherian Normalization Lemma, $L/k$ is finite field extension.
    Note that geometrically integral if and only if $k$ is algebraically closed in function field $k(X)$.
    Get $L = k$.
\end{reason}
\begin{corollary}
    Let $A$ be a noetherian ring, $X$ proper over $\spec A$, $\mathcal{L}$ ample invertible sheaf on $X$.
    Then for all $\mathcal{F}$ coherent sheaf on $X$, there exists $n_{0}$ relative to $\mathcal{F}$ such that $H^{i}(X, \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n}) = 0$ for all $i > 0$ and $n \ge n_{0}$. 
    \label{Corollary 2.10}
\end{corollary}
\begin{reason}
    Note that there exists $m > 0$ such that $\mathcal{L}^{m}$ is very ample.
    Get closed immersion $i: X \hookrightarrow \mathbb{P}_{A}^{r}$ such that $\mathcal{L}^{n} = \mathcal{O}_{X}(1)$.
    Apply Theorem \ref{Theorem 2.7} to $\mathcal{F}, \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}, \cdots, \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{m - 1}$.
\end{reason}
\begin{theorem}[\textbf{\emph{Serre Cohomological Criteria for Ampleness}}]
    Let $A$ be a noetherian ring, $X$ proper over $\spec A$, $\mathcal{L}$ invertible sheaf on $X$.
    Then the following conditions are equivalent \\
    (1)$\mathcal{L}$ is ample \\
    (2)for all $\mathcal{F}$ coherent sheaf on $X$, 
    there exists $n_{0}$ relative to $\mathcal{F}$ such that $H^{i}(X, \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n}) = 0$ for all $i > 0$ and $n \ge n_{0}$. \\
    (3)for all $\mathcal{F}$ coherent sheaf on $X$, 
    there exists $n_{0}$ relative to $\mathcal{F}$ such that $H^{1}(X, \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n}) = 0$.
    \vspace{-\baselineskip} % 减少一行间距
    \label{Theorem 2.8}
\end{theorem}
\begin{proof}
    Step 1.
    Since by Corollary \ref{Corollary 2.10}, we have $(1) \Rightarrow (2)$, and $(2) \Rightarrow (3)$ is obvious.
    Only need to prove $(3) \Rightarrow (1)$.
    Moreover, suffices to prove that for all $\mathcal{F}$ coherent sheaf on $X$ and closed point $x\in X$,
    there exists open neighbourhood $U_{x}\ni x$ and $n_{0}(x) > 0$ such that for all $n \ge n_{0}(x)$ and $y\in U_{x}$,
    the stalk $(\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})_{y}$ is generated by global sections of $\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n}$,
    since $X$ noetherian, it can be covered by only finitely many $U_{x}$ so that we can take a uniform upper bound of $n_{0}(x)$.
    \par
    Step 2.
    Claim that it suffices to prove that for all $\mathcal{F}$ coherent sheaf on $X$, closed point $x\in X$ and large enough $n$,
    there exists open neighbourhood $U_{x}\ni x$ depending on $n$ such that for all  $y\in U_{x}$,
    the stalk $(\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})_{y}$ is generated by global sections of $\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n}$.
    Assume we have proved this.
    Apply it to $\mathcal{F} = \mathcal{O}_{X}$, there exists large enough $n_{1}$ and $V\ni x$ such that for all $y\in V$, $(\mathcal{L}^{n_{1}})_{y}$ is generated by global sections.
    Then apply this to $\mathcal{F}$, there exists large enough $n_{0}$ and open neighbourhoods $U_{0}, U_{1}, \cdots, U_{n_{1} - 1}$ of $x$ such that for all $i$ and $y\in U_{i}$,
    $(\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n + i})_{y}$ is generated by global sections.
    Take $U_{x} = V \cap U_{0} \cap \cdots \cap U_{n_{1} - 1}$.
    For all $n \ge n_{0}$ and $y\in U_{x}$, assume $n = n_{0} + mn_{1} + i$, 
    then $(\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})_{y} = (\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n_{0} + i})_{y} \otimes_{\mathcal{O}_{X, y}} (\mathcal{L}^{n_{1}})_{y}^{\otimes m}$ is generated by global sections.
    \par
    Step 3.
    Let $x\in X$ be a closed point, $\mathcal{I}_{x}$ the ideal sheaf of $\{x\} \overset{i}{\hookrightarrow} X$,
    where $\{x\}$ has the same scheme structure as $\spec(k(x))$ with structure sheaf denoted by $k(x)$ for convenience.
    We have short exact sequence
    \begin{equation}
        0 \longrightarrow \mathcal{I}_{X} \longrightarrow \mathcal{O}_{x} \longrightarrow i_{\ast}k(x) \longrightarrow 0
    \end{equation}
    Tensor by $\mathcal{F}$, get
    \begin{equation}
        \mathcal{I}_{x}\mathcal{F} \longrightarrow \mathcal{F} \longrightarrow i_{\ast}k(x) \otimes_{\mathcal{O}_{X}} \mathcal{F} \longrightarrow 0
    \end{equation}
    Tensor by $\mathcal{L}^{r}$, get
    \begin{equation}
        \mathcal{I}_{x}\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n} \longrightarrow \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n} \longrightarrow i_{\ast}k(x) \otimes_{\mathcal{O}_{X}} \mathcal{F} \otimes_{\mathcal{O}_{x}} \mathcal{L}^{n}\longrightarrow 0
    \end{equation}
    Note that, by hypothesis, $H^{1}(X, \mathcal{I}_{X}\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n}) = 0$ for all $n \ge n_{0}$.
    So $\Gamma(X, \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n}) \longrightarrow \Gamma(X, i_{\ast}k(x) \otimes_{\mathcal{O}_{X}} \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})$ is surjective for all $n \ge n_{0}$.
    Note that $i_{\ast}k(x) \otimes_{\mathcal{O}_{X}} \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n}$ is only supported at $x$,
    we have that $\Gamma(X, i_{\ast}k(x) \otimes_{\mathcal{O}_{X}} \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n}) = (i_{\ast}k(x) \otimes_{\mathcal{O}_{X}} \mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})_{x} = k(x) \otimes_{\mathcal{O}_{X, x}} (\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})_{x}$.
    Denote $(\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})_{x}$ by $M$.
    As $M/\mathfrak{m}_{x}M$ is generated by global sections, by Nakayama's Lemma, $M$ is generated by global sections.
    \par
    As $\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n}$ is coherent,
    take an affine open neighbourhood $U = \spec A$ of $x$ so that $(\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})\big{|}_{U} = \widetilde{N}$ for some finitely generated $A$-module.
    Assume $x$ corresponds to maximal ideal $\mathfrak{m}$ and $N$ is generated by $m_{1}, \cdots, m_{l}$.
    Since $N_{\mathfrak{m}}$ is generated by global sections, $\frac{m_{k}}{1} = \frac{\sum_{j} a_{kj}s_{j, x}}{b_{k}}$,
    where $a_{kj}\in A$, $b_{k}\notin \mathfrak{m}$ and $s_{j}$ are global sections.
    Then there exists $c_{k}\notin \mathfrak{m}$ such that $(b_{k}m_{k} - \sum_{j} a_{kj}s_{j, x})c_{k} = 0$.
    Consider $b = \prod_{k = 1}^{l} b_{k}c_{k}$, then $\mathfrak{m}\in D(b)$.
    Obviously, for each $\mathfrak{p}\in D(b)$, $\frac{m_{k}}{1}$ can be generated by global sections in $N_{\mathfrak{p}}$.
    Thus for all $n \ge n_{0}$, there exists open neighbourhood $U_{x}\ni x$ depending on $n$ such that for all $y\in U_{x}$,
    $(\mathcal{F} \otimes_{\mathcal{O}_{X}} \mathcal{L}^{n})_{y}$ is generated by global sections, done!
\end{proof}
\begin{remark}
    In fact, all finiteness results still hold for $X$ proper over $A$.
    Proofs can be seen in EGA or Stacks Project.
\end{remark}

\section{Riemann-Roch Formula}
\label{section:Riemann-Roch_Formula}

\subsection{Serre's duality}
\label{subsection:Riemann-Roch_Formula_Serre's_duality}

\begin{definition}
    Let $X$ be a variety, $\mathcal{F}\in \abeliangroups (X)$.
    Define the Euler characteristic of $\mathcal{F}$ to be $\chi(\mathcal{F}) := \sum_{i \ge 0} (-1)^{i} \cdot h^{i}(X, \mathcal{F})$,
    which is in fact a finite sum by Grothendieck Vanishing Theorem.
\end{definition}
\begin{lemma}
    Let $X$ be a variety.
    Then for all short exact sequence $0 \rightarrow \mathcal{F}' \rightarrow \mathcal{F} \rightarrow \mathcal{F}'' \rightarrow 0$ in $\abeliangroups (X)$,
    we have that $\chi(\mathcal{F}) = \chi(\mathcal{F}') + \chi(\mathcal{F}'')$.
    \label{Lemma 3.1}
\end{lemma}
\begin{proof}
    Applying global section functor, we get a long exact sequence
    \begin{equation}
        0 \rightarrow H^{0}(X, \mathcal{F}') \rightarrow H^{0}(X, \mathcal{F}) \rightarrow H^{0}(X, \mathcal{F}'') \rightarrow H^{1}(X, \mathcal{F}') \rightarrow \cdots 
    \end{equation}
    By Grothendieck Vanishing Theorem, this sequence would end for some $n$ large enough.
    Then we can split it into several short exact sequences.
    Summing the equations of dimensions given by these short exact sequence, we are done!
\end{proof}
\begin{theorem}[\textbf{\emph{Serre's Duality}}]
    Let $X$ be a smooth projective variety of dimension $n$, $\omega_{X}$ canonical sheaf.
    Then for all locally free sheaf $\mathcal{F}$ on $X$, we have canonical isomorphism $H^{i}(X, \mathcal{F}^{\vee} \otimes \omega_{X}) \overset{\sim}{\rightarrow} H^{n - i}(X, \mathcal{F})^{\vee}$.
    \label{Theorem 3.1}
\end{theorem}
\begin{remark}
    In class, Professor Du gave a proof as following.
    First take injective resolutions $\mathcal{I}^{\bullet}$ of $\mathcal{F}$, then tensor with $\omega_{X}$.
    Since $\omega_{X}$ is flat, we $0 \rightarrow \mathcal{F} \otimes \omega_{X} \rightarrow \mathcal{I}^{\bullet} \otimes \omega_{X}$ is still exact.
    However, we do not know if $\mathcal{I} \otimes \omega_{X}$ is still injective.
\end{remark}
\begin{corollary}
    Let $X$ be a smooth projective variety of dimension $n$, $\omega_{X}$ canonical sheaf.
    Then for all locally free sheaf $\mathcal{F}$ on $X$, $\chi(\mathcal{F}) = (-1)^{n} \cdot \chi(\mathcal{F}^{\vee} \otimes \omega_{X})$.
    \label{Corollary 3.1}  
\end{corollary}
\begin{proof}
    Immediately comes from Grothendieck Vanishing and Serre's duality.
\end{proof}

\subsection{Riemann-Roch for curves}
\label{subsection:Riemann-Roch_for_curves}

\begin{proposition}
    Let $X$ be an integral variety, $\mathcal{F}\in \coherent (X)$.
    Then there exists open dense subset $U \subseteq X$ such that $\mathcal{F}\big{|}_{U}$ is locally free.
    Moreover, we can well define $\rank (\mathcal{F}) := \rank (\mathcal{F}\big{|}_{U})$.
    \label{Proposition 3.1}
\end{proposition}
\begin{proof}
    Consider the subset $\{x\in X \big{|} \dim_{k(x)} \mathcal{F}_{x}/\mathfrak{m}_{x}\mathcal{F}_{x} \le d\}$,
    which by Nakayama's Lemma is an open subset.
    Then we may take $d$ minimal so that $U := \{x\in X \big{|} \dim_{k(x)} \mathcal{F}_{x}/\mathfrak{m}_{x}\mathcal{F}_{x} = d\}$ is an open subset.
    Since $X$ is integral, $U$ is irreducible.
    \par
    Now we want to show that $\mathcal{F}\big{|}_{U}$ is locally free.
    Take affine subset $W = \spec A$ such that $\mathcal{F}\big{|}_{W} = \widetilde{M}$ for some finitely generated $A$-module $M$.
    Then for all $\mathfrak{p}\in \spec A$, $M_{\mathfrak{p}}$ is generated by exact $d$ elements.
    \par
    Narrowing $W$, we may assume that there exists $m_{1}, \cdots, m_{d}$ in $M$ such that $M_{\mathfrak{p}}$ can be generated by them for all $\mathfrak{p}\in \spec A$.
    Then if there is some relation $\sum_{i = 1}^{d} a_{i}m_{i} = 0$,
    then $a_{i}\in \mathfrak{R}(A) = (0)$ for all $i$.
    Otherwise, there exists $\mathfrak{q}\in \spec A$ such that $a_{i}\notin \mathfrak{q}$ for some $i$.
    And then this relation becomes a relation in $M_{\mathfrak{q}} \otimes A_{\mathfrak{q}}/\mathfrak{q}A_{\mathfrak{q}}$, contradicting to $\mathfrak{q}\in U$.
    Hence $\mathcal{F}\big{|}_{W}$ is free and $\mathcal{F}\big{|}_{U}$ is locally free.
\end{proof}
\begin{lemma}
    Let $X$ be an integral variety.
    Then for all short exact sequence $0 \rightarrow \mathcal{F}' \rightarrow \mathcal{F} \rightarrow \mathcal{F}'' \rightarrow 0$ in $\coherent (X)$,
    we have that $\rank (\mathcal{F}) = \rank (\mathcal{F}') + \rank (\mathcal{F}'')$.
    \label{Lemma 3.2}
\end{lemma}
\begin{proof}
    We may take open dense subset $U \subseteq X$ such that $\mathcal{F}\big{|}_{U}$, $\mathcal{F}'\big{|}_{U}$ and $\mathcal{F}''\big{|}_{U}$ are all locally free.
    Then it is clear that $\rank (\mathcal{F}\big{|}_{U}) = \rank (\mathcal{F}'\big{|}_{U}) + \rank (\mathcal{F}''\big{|}_{U})$.
\end{proof}
\begin{definition}
    Let $X$ be an integral variety, $\mathcal{F}\in \coherent (X)$.
    Define $\deg (\mathcal{F}) = \chi(\mathcal{F}) - \rank \cdot \chi(\mathcal{O}_{X})$.
\end{definition}
\begin{lemma}
    Let $X$ be an integral variety.
    Then for all short exact sequence $0 \rightarrow \mathcal{F}' \rightarrow \mathcal{F} \rightarrow \mathcal{F}'' \rightarrow 0$ in $\coherent (X)$,
    we have that $\deg (\mathcal{F}) = \deg (\mathcal{F}') + \deg (\mathcal{F}'')$.
    \label{Lemma 3.3}
\end{lemma}
\begin{reason}
    Immediately comes from Lemma \ref{Lemma 3.1} and Lemma \ref{Lemma 3.2}
\end{reason}
Now let $C$ be a smooth connected projective curve.
Define the (arithmatic) genus of $C$ to be $g(C) := 1 - \chi(C) = h^{1}(C, \mathcal{O}_{C})$.
\begin{proposition}
    Let $C \subseteq \mathbb{P}_{\mathbb{C}}^{2}$ be a smooth curve of degree $n$.
    Then $C$ is connected and $g(C) = \frac{(n - 1)(n - 2)}{2}$.
    \label{Proposition 3.2}
\end{proposition}
\begin{proof}
    Assume $C = V(f)$ with $\deg f = n$.
    Consider exact sequence $0 \rightarrow \mathcal{O}_{\mathbb{P}_{\mathbb{C}}^{2}}(-n) \overset{\cdot f}{\rightarrow} \mathcal{O}_{\mathbb{P}_{\mathbb{C}}^{2}} \rightarrow \mathcal{O}_{C} \rightarrow 0$.
    Then $\chi(\mathcal{O}_{C}) = \chi(\mathcal{O}_{\mathbb{P}_{\mathbb{C}}^{2}}) - \chi(\mathcal{O}_{\mathbb{P}_{\mathbb{C}}^{2}}(-n))$.
    Since $\chi(\mathcal{O}_{\mathbb{P}_{\mathbb{C}^{2}}}) = h^{0}(\mathcal{O}_{\mathbb{P}_{\mathbb{C}^{2}}}) = 1$ and by Serre's duality,
    $\chi(\mathcal{O}_{\mathbb{P}_{\mathbb{C}^{2}}}(-n)) = -h^{1}(\mathcal{O}_{\mathbb{P}_{\mathbb{C}^{2}}}(-n)) = -h^{1}(\mathcal{O}_{\mathbb{P}_{\mathbb{C}^{2}}}(-n))^{\vee} = -h^{0}(\mathcal{O}_{\mathbb{P}_{\mathbb{C}^{2}}}(n - 3)) = -\frac{(n - 1)(n - 2)}{2}$,
    we get that $g(C) = \frac{(n - 1)(n - 2)}{2}$.
\end{proof}
\begin{remark}
    Connectedness comes from the fact that every two different curves in $\mathbb{P}_{\mathbb{C}}^{2}$ would intersect,
    in which case smoothness implies irreducibility.
\end{remark}
Let $D = \sum_{i} a_{i}x_{i}$ be an effective Weil divisor on $C$.
Define the degree of $D$ to be $\deg D = \sum_{i} a_{i}$.
\begin{proposition}
    Every effective Weil divisor $D$ would correspond to an invertible sheaf $\mathcal{O}_{X}(D)$.
    Moreover, $\mathcal{O}_{X}(D_{1}) \cong \mathcal{O}_{X}(D_{2})$ if and only if $D_{1} \sim D_{2}$.
    \label{Proposition 3.3}
\end{proposition} 
\begin{proof}
    Consider $X_{i} = \spec \mathcal{O}_{X, x_{i}}/\mathfrak{m}_{x_{i}}^{a_{i}}$.
    Then there are closed immersions $\varphi_{i}: X_{i} \hookrightarrow \spec X$.
    Taking disjoint product $Y := \sqcup X_{i}$, we get a closed subscheme of $X$.
    Consider the ideal sheaf $\mathcal{O}_{X}(-D) := \mathcal{I}_{Y/X}$.
    And our desired $\mathcal{O}_{X}(D)$ can be defined as dual of $\mathcal{O}_{X}(-D)$.
    \par
    Now we are supposed to show that $\mathcal{O}_{X}(-D)$ is locally free of rank $1$.
    Affine locally, we have $U = \spec A$ and $X_{i} = \spec A/\mathfrak{p}_{i}^{a_{i}}$.
    Then $Y = \sqcup X_{i} = \spec \bigoplus A/\mathfrak{p}_{i}^{a_{i}} \cong \spec A/\prod \mathfrak{p}_{i}^{a_{i}}$ and $\mathcal{I}_{Y/X}\big{|}_{U} = \prod \mathfrak{p}_{i}^{a_{i}}$.
    \par
    Note that $C$ is smooth, for all $i$, $A_{\mathfrak{p}_{i}}$ is a DVR.
    Take uniformizers $\varpi_{i}\in A_{\mathfrak{p}_{i}}$.
    Then there exists open subset $W = D(s) \subseteq U$ such that $\varpi_{i}\in A_{s}$.
    Thus $\mathfrak{p}_{i}A_{s}$ is a principle ideal generated by $\varpi_{i}$ and so is $\prod \mathfrak{p}_{i}^{a_{i}}$.
    Conclude that $\mathcal{O}_{X}(-D)$ is locally free of rank $1$.
\end{proof}
\begin{remark}
    For arbitrary Weil divisor $D$, we can write $D = D_{1} - D_{2}$ with $D_{1}$ and $D_{2}$ effective.
    Then define $\mathcal{O}_{X}(D) = \mathcal{O}_{X}(D_{1}) \otimes \mathcal{O}_{X}(-D_{2})$.
    In addition, the second part comes from careful argument about transition functions.
\end{remark}
\begin{lemma}
    $\deg D = \deg (\mathcal{O}_{X}(D))$ for all Weil divisor $D$.
    \label{Lemma 3.4}
\end{lemma}
\begin{proof}
    First prove for effective $D$.
    Take $\ell: Y \rightarrow X$ as above, then there is an exact sequence
    \begin{equation}
        0 \longrightarrow \mathcal{O}_{X}(-D) \longrightarrow \mathcal{O}_{X} \longrightarrow \ell_{\ast}\mathcal{O}_{Y} \longrightarrow 0
    \end{equation}
    Tensoring by $\mathcal{O}_{X}(D)$, we get exact sequence
    \begin{equation}
        0 \longrightarrow \mathcal{O}_{X} \longrightarrow \mathcal{O}_{X}(D) \longrightarrow \ell_{\ast}\mathcal{O}_{Y}(D) \longrightarrow 0
    \end{equation}
    Then by Lemma \ref{Lemma 3.1}, $\deg (\mathcal{O}_{X}(D)) = \chi(\mathcal{O}_{X}(D)) - \chi(\mathcal{O}_{X}) = \chi(\ell_{\ast}\mathcal{O}_{Y}(D))$.
    Is suffices to show $\chi(\ell_{\ast}\mathcal{O}_{Y} \otimes \mathcal{O}_{X}(D)) = \deg D$.
    Note that we can take affine open covering $\mathcal{U}$ of $X$ trivializing $\mathcal{O}_{X}(D)$ such that for all $i$, there is a unique $U_{i} = \spec A_{i}$ in $\mathcal{U}$ containing $x_{i}$.
    \par
    Use such a covering to compute cohomology.
    Since $\ell_{\ast}\mathcal{O}_{Y} = \oplus \ell_{\ast}\mathcal{O}_{X_{i}}$,
    $\chi(\ell_{\ast}\mathcal{O}_{Y}(D)) = \sum \chi(\ell_{\ast}\mathcal{O}_{X_{i}}(D))$.
    It is clear that $\Gamma(X, \ell_{\ast}\mathcal{O}_{X_{i}}(D)) \cong \Gamma(U_{i}, \ell_{\ast}\mathcal{O}_{X_{i}}(D))$.
    Thus $\chi(\ell_{\ast}\mathcal{O}_{X_{i}}(D)) = a_{i} - 0 = a_{i}$ and hence $\chi\ell_{\ast}\mathcal{O}_{Y}(D) = \sum a_{i} = \deg D$.
    \par
    For arbitrary $D$, write $D = D_{1} - D_{2}$ with $D_{1}$ and $D_{2}$ effective.
    Then $\deg D = \deg D_{1} - \deg D_{2} = \deg (\mathcal{O}_{X}(D_{1})) - \deg (\mathcal{O}_{X}(D_{2})) = \chi(\mathcal{O}_{X}(D_{1})) - \chi(\mathcal{O}_{X}(D_{2}))$.
    Consider exact sequence
    \begin{equation}
        0 \longrightarrow \mathcal{O}_{X}(D_{1} - D_{2}) \longrightarrow \mathcal{O}_{X}(D_{1}) \longrightarrow \mathcal{O}_{D_{2}}(D_{1}) \longrightarrow 0
    \end{equation}
    By similar argument, we know $\chi(\mathcal{O}_{X}(D)) = \chi(\mathcal{O}_{X}(D_{1})) - \deg D_{2} = \chi(\mathcal{O}_{X}(D_{1})) - \chi(\mathcal{O}_{X}(D_{2})) + \chi(\mathcal{O}_{X})$.
    Thus $\deg D = \deg (\mathcal{O}_{X}(D))$.
\end{proof}
\begin{corollary}
    The map $\deg: \picardscheme (X) \rightarrow \mathbb{Z}$ is a group homomorphism.
    \label{Corollary 3.2}
\end{corollary}
\begin{reason}
    Immediately comes from the fact that $\deg: WeilDiv \rightarrow \mathbb{Z}$ is a group homomorphism and Lemma \ref{Lemma 3.4}.
\end{reason}
\begin{lemma}
    Let $\mathcal{L}$ be an invertible sheaf on $X$.
    Then for all nonzero global section $s$ of $\mathcal{L}$, we have that $\mathcal{O}_{X}(\divisor s) \cong \mathcal{L}$.
    \label{Lemma 3.5}
\end{lemma}
\begin{proof}
    Assume $g_{ij}$ are transition functions of $\mathcal{L}$ and $s\big{|}_{U_{i}} = f_{i}e_{i}$ where $e_{i}$ has image $1$ under trivialization.
    Then we have that $f_{j}e_{j} = f_{j}g_{ij}e_{i}$ so that $f_{i} = g_{ij}f_{j}$ on $U_{i} \cap U_{j}$.
    By definition, $\div s = (U_{i}, f_{i})$ and $\mathcal{O}_{X}(\div s)$ is defined by transition functions $\frac{f_{i}}{f_{j}} = g_{ij}$.
    Hence $\mathcal{O}_{X}(\div s) \cong \mathcal{L}$.
\end{proof}
\begin{corollary}
    Let $\mathcal{L}$ be an invertible sheaf on $X$.
    If $H^{0}(X, \mathcal{L}) \neq 0$, then $\deg L \ge 0$.
    \label{Corollary 3.3}
\end{corollary}
\begin{reason}
    By Lemma \ref{Lemma 3.5}, pick a nonzero global section $s$ of $\mathcal{L}$,
    then we know $\mathcal{L} \cong \mathcal{O}_{X}(\div s)$.
    Note that $s$ has no pole, $\div s$ is an effective Weil divisor so that $\deg \mathcal{L} = \deg \mathcal{O}_{X}(\div s) = \deg (\div s) \ge 0$.
\end{reason}

\subsection{Grothendieck group}
\label{subsection:Riemann-Roch_for_curves_Grothendieck_group}

\begin{definition}
    Let $X$ be a variety.
    Define the Grothendieck group $K(X)$ (resp. $K_{0}(X)$) to be the quotient group of the free group spanned by the coherent sheaves (resp. locally free sheaves of finite rank) by the subgroup spanned by elements of the form $\mathcal{F} - \mathcal{F}' - \mathcal{F}''$ for short exact sequence $0 \rightarrow \mathcal{F}' \rightarrow \mathcal{F} \rightarrow \mathcal{F}'' \rightarrow 0$.
\end{definition}
\begin{remark}
    There is a natural homomorphism $i: K_{0}(X) \rightarrow K(X)$ sending $\overline{\mathcal{E}}$ to $\overline{\mathcal{E}}$.
\end{remark}
\begin{lemma}
    Let $X$ be a regular projective curve, $\mathcal{F}\in \coherent (X)$.
    Then there is an exact sequence $0 \rightarrow \mathcal{E}_{1} \rightarrow \mathcal{E}_{2} \rightarrow \mathcal{F} \rightarrow X$ with $\mathcal{E}_{1}$ and $\mathcal{E}_{2}$ locally free of finite rank.
    \label{Lemma 3.6}
\end{lemma}
\begin{proof}
    Since $X$ is projective, there is a very ample line bundle $\mathcal{O}_{X}(1)$.
    Then by Corollary \ref{Corollary 1.1}, there is a surjection $\mathcal{O}_{X}(m)^{\oplus r} \twoheadrightarrow \mathcal{F}$.
    Set $\mathcal{E}_{1} = \mathcal{O}_{X}(m)^{\oplus r}$, consider kernel $\mathcal{E}_{2}$.
    Want to show that $\mathcal{E}_{2}$ is locally free.
    In fact, since for all closed point $x\in X$, $\mathcal{O}_{X, x}$ is a DVR and hence PID.
    As $\mathcal{E}_{2, x}$ is a submodule of $\mathcal{E}_{1, x}$ which is free, we get $\mathcal{E}_{2, x}$ also free.
    Hence $\mathcal{E}_{2}$ is locally free of finite rank. 
\end{proof}
\begin{proposition}
    Let $X$ be a regular projective curve.
    Then $i: K_{0}(X) \rightarrow K(X)$ is a group isomorphism.
    \label{Proposition 3.4}
\end{proposition}
\begin{proof}
    First to show that $i$ is surjective.
    For all $\mathcal{F}\in \coherent (X)$, by Lemma \ref{Lemma 3.5},
    there is a short exact sequence
    \begin{equation}
        0 \longrightarrow \mathcal{E}_{2} \overset{\varphi_{2}}{\longrightarrow} \mathcal{E}_{1} \overset{\varphi_{1}}{\longrightarrow} \mathcal{F} \longrightarrow 0
    \end{equation}
    with $\mathcal{E}_{1}$ and $\mathcal{E}_{2}$ locally free of finite rank.
    Then we get $\overline{\mathcal{F}} = \overline{\mathcal{E}_{1} - \mathcal{E}_{2}}$ so that $i$ is surjective.
    \par
    Conversely, it is natural to define $j: K(X) \rightarrow K_{0}(X)$ sending $\overline{\mathcal{F}}$ to $\overline{\mathcal{E}_{1} - \mathcal{E}_{2}}$.
    Given another exact sequence
    \begin{equation}
        0 \longrightarrow \mathcal{E}_{2}' \overset{\psi_{2}}{\longrightarrow} \mathcal{E}_{1}' \overset{\psi_{1}}{\longrightarrow} \mathcal{F} \longrightarrow 0
    \end{equation}
\end{proof}
\begin{corollary}
    Let $X$ be a regular projective curve.
    Then $K(X)$ admits a ring structure with multiplication induced by tensor product of locally free sheaves,
    callled the Grothendieck ring of $X$.
    \label{Corollary 3.4}
\end{corollary}
\begin{corollary}
    Let $X$ be a regular projective curve.
    Then $K(X) \overset{j}{\rightarrow} K_{0}(X) \overset{\det}{\rightarrow} \picardscheme (X)$ is a group homomorphism.
    \label{Corollary 3.5}
\end{corollary}
\begin{lemma}
    Let $X$ be a regular projective curve.
    Put $A(X) := \mathbb{Z} \langle \mathcal{O}_{p} \big{|} p\in X \rangle/\sim$.
    \label{Lemma 3.7}
\end{lemma}
\begin{theorem}
    Let $X$ be a regular projective curve, $\mathcal{F}\in \coherent (X)$.
    Then $\deg \mathcal{F} = \deg (\det \mathcal{F})$.
    \label{Theorem 3.2}
\end{theorem}
\begin{proof}
    Note that $\deg: K(X) \rightarrow \mathbb{Z}$ is a group homomorphism,
    suffices to check for generators of $K(X)$ i.e. locally free sheaves of finite rank.
    
    Then $A(X)$ is a subgroup of $K(X)$ and $K(X) \cong A(X) \oplus \mathbb{Z}$.

\end{proof}
\end{document}